---
title: "rad_clustering_BAD!!!!"
author: "Kyle"
date: "2024-01-19"
output: html_document
---

```{r setup, include=FALSE}
.libPaths("/g/data/nm24/Overt_pheno_rlibs")

#library(ConsensusClusterPlus)
library(dplyr)
library(readr)
library(tidyverse)
library(janitor)
library(viridisLite)
#library(ggpmisc)
library(ggplot2)
library(stringr)
library(dbscan)
library(RColorBrewer)
library(slanter)
library(broom)
library(ggforce)
library(parallel)
library(pbapply)
library(data.table)
library(Rmisc)
library(pheatmap)
library(factoextra)
library(igraph)
#library(multcomp)
library(emmeans)
#library(ResourceSelection)
library(car)
library(multcompView)
library(glmnet)
library(MuMIn)
knitr::opts_chunk$set(echo = TRUE)
library(combinat)
library(performance)
library(cluster)
# gets the position to place the number of positive features (above max point)
n_fun_pos <- function(x){
  return(data.frame(y = max(x), label = paste0(length(x))))
}

# same as above but for negative features
n_fun_neg <- function(x){
  return(data.frame(y = min(x), label = paste0(length(x))))
}

# normalise data but isn't yet used... radiomics_data is already normalised... 
normalise_2 <- function(x, df, na.rm = FALSE) {
  res <- x/df$WEV
  return(res)
  
  }

scale_to_mm <- function(x) {
  um_conv_factor <- 40
  um_to_mm_conv_factor <- 1e3
  return((x*um_conv_factor)/um_to_mm_conv_factor)
}


scale_to_mm3 <- function(x) {
  #voxel size is 40um 
  um3_conv_factor <- 40.0^3  # To convert voxels to um3
  um3_to_mm3_conv_factor <- 1e9
  return((x * um3_conv_factor)/um3_to_mm3_conv_factor)
}


# prepares the data by arranging the variables and getting the genotype, background and WEV columns 
prep_data <- function(rad_str, staging_str){
  
  rad_info <- read_csv(rad_str)

  
  staging_info <- read_csv(staging_str)
  
  rad_info <- merge(rad_info, staging_info[c(1,2,3,4)], by.x = 'vol', by.y = 'vol', all.x = F, all.y=F) %>% dplyr::select(-c(staging,line))
  

  rad_info <- rad_info %>% remove_constant() %>% mutate_at(vars(contains('WEV')|contains('Volume')), scale_to_mm3) 
  
  rad_info <- rad_info %>% remove_constant() %>% mutate_at(vars(contains('Length')), scale_to_mm3) 
  
  
  rad_info <- rad_info %>% dplyr::mutate(dplyr::across(where(is.numeric) & !matches('org') & !matches('WEV'), ~ normalise_2(.x, df = rad_info)))
  
  
  #rad_info$Genotype <- factor(rad_info$Genotype, levels = c("WT", "HET"))
  
  #rad_info$Background <- factor(rad_info$Background, levels = c("C3H", "C57BL6"))

  rad_info <- dplyr::arrange(transform(rad_info, Background=ordered(Background,levels=c("C3H","C57BL6"))))
  
  rad_info <- dplyr::arrange(transform(rad_info, Genotype=ordered(Genotype,levels=c("WT","HET"))))
  return(rad_info)
}

# fixes the column labels and replaces the number with the organ name. 
fix_column_labels <- function(rad_data){
  
  rad_info_colnames <- colnames(rad_data)
  
  mapping <- data.frame(label = label_info$label, label_name = label_info$label_name)
  
  numbers <- as.numeric(gsub(".*__([0-9]+)$", "\\1", rad_info_colnames))
  
  
  match_indices <- match(numbers, as.integer(mapping$label))
  for (i in 1:length(rad_info_colnames)) {
    if (!is.na(match_indices[i])) {
      rad_info_colnames[i] <- gsub("__[0-9]+$", paste0(" ", mapping$label_name[match_indices[i]]), rad_info_colnames[i])}
    }
  
  rad_info_colnames <- str_replace(rad_info_colnames, " ", "_")
  
  colnames(rad_data) <- rad_info_colnames
  
  return(rad_data)
  
}

# fits a two-way linear model and returns the tvals and pvals from the model
g_by_e_lm <- function(y, dataset, pair_test=F){
  if (pair_test){
    library(mixlm)
    #Had to transform the data to not get residuals adding to 0? 
    model <- lm(I(y * 1e8)~Genotype:Background+Genotype+Background+WEV, data=dataset)
    pair_model <- simple.glht(model,'Background')
    #print("it's me")
    pvals <- pair_model$res$'P(>t)'
    names(pvals) <- rownames(pair_model$res)
    #gets p and t vals from model
    #results <- list(pvals=pair_model$res$'P(>t)', tvals=pair_model$res$'t value')
    detach("package:mixlm", unload=T)
    library(stats)
    return(pvals)
  }
  else{
    #dataset$Genotype <- factor(dataset$Genotype, ordered=F)
    #dataset$Background <- factor
    #model for stats
    model <- stats::lm(y~Genotype:Background+Genotype*Background+WEV, data=dataset)
    #model 
    
    results <- pandt_vals(model)
    pvals <- results$pvals
    tvals <- results$tvals
    names(pvals) <- names(model$coefficients)
    names(tvals) <- names(model$coefficients)
    list(pvals=pvals, tvals=tvals)
  }
}


# function to return p and tvals from the model
pandt_vals <- function(fit) {
  # so for some reason these are not two dimensional and only 1d
  
  # get estimates
  est <- fit$coefficients[fit$qr$pivot]
  
  # get R: see stats:::summary.lm to see how this is calculated
  p1 <- 1L:(fit$rank)
  R <- diag(chol2inv(fit$qr$qr[p1, p1, drop = FALSE]))
  
  # get residual sum of squares for each
  resvar <- sum(fit$residuals^2) / fit$df.residual
  # R is same for each coefficient, resvar is same within each model 
  se <- sqrt(outer(R, resvar))
  
  tvals <- est / se
  pvals <- pt(abs(est / se), df = fit$df.residual, lower.tail = FALSE) * 2
  
  return(list(pvals=pvals, tvals=tvals))
}


# relabel tvals and pvals 
relabel_df <- function(df, pvals){
  # Assign row names (coefficient names) from the first element of the list
  rownames(df) <- names(pvals[[1]]$pvals)
  # Assign column names using the names of the list elements (sample names)
  colnames(df) <- names(pvals)
  return(df)
}

# used to multiple word organ labels (within a the column) into a single vector
merge_after_third <- function(vec) {
  vec[4] <- paste(vec[4:length(vec)], collapse = " ")
  vec <- vec[1:4]
  return(vec)
}


create_cluster_df <- function(dataset){
  
  if (length(names(dataset) > 0)) {
    split_names <- strsplit(names(dataset), "_")
  
  split_names <- lapply(split_names, function(x) {
    if ("wavelet" %in% x) {x <- x[c(-1)]}
    return(x)})
  
  split_names <- lapply(split_names, merge_after_third)
  
  cluster_df <- data.frame(matrix(unlist(split_names), nrow=length(split_names), byrow=TRUE))
  
  
  colnames(cluster_df) <- c("Filter", "Type", "Stat", "Org")}
  
  else {
    cluster_df <- data.frame(matrix(ncol = 4, nrow = 0))
    colnames(cluster_df) <- c("Filter", "Type", "Stat", "Org")
  }
  
  return(cluster_df)
}


combine_rows_to_vector <- function(df) {
  # Apply the function to each row, pasting the values together
  combined_column <- apply(df, 1, function(row) str_replace_all(paste(row, collapse = "_")," ", "_"))
  
  # Convert to a dataframe
  #combined_df <- data.frame(Combined = combined_column, stringsAsFactors = FALSE)
  
  return(combined_column)
}


pairwise_fisher <- function(table) {
  # Get unique Org levels
  org_levels <- unique(table$Org)
  
  # Create an empty matrix to store p-values
  p_matrix <- matrix(NA, nrow = length(org_levels), ncol = length(org_levels),
                     dimnames = list(org_levels, org_levels))
  
  # Loop over all pairs of Org levels
  for (i in 1:(length(org_levels)-1)) {
    for (j in (i+1):length(org_levels)) {
      # Subset the table to include only rows for the current pair of Orgs
      pair_table <- table %>% filter(Org %in% c(org_levels[i], org_levels[j]))
      
      # Aggregate data for contingency table
      table_summary <- aggregate(cbind(Freq, Non_Counts) ~ Org, data = pair_table, FUN = sum)
      
      # Create the contingency table
      contingency_table <- as.matrix(table_summary[, c("Freq", "Non_Counts")])
      
      # Perform Fisher's exact test
      fisher_test <- fisher.test(contingency_table)
      
      # Store the p-value in the matrix
      p_matrix[i, j] <- fisher_test$p.value
      p_matrix[j, i] <- fisher_test$p.value  # Fill the symmetric value
    }
  }
  
  return(p_matrix)
}



#USE THIS FUNCTION AND DON'T MESS WITH IT, I DARE YOU TO TRY
# AND MERGE THE COLUMNS WITHOUT STUPID SHIT HAPPENING

expand_counts_table <- function(counts_table) {
  # Create an empty dataframe to store expanded rows
  expanded_table <- data.frame()
  
  # Loop over each row in the counts_table
  for (i in 1:nrow(counts_table)) {
    row <- counts_table[i, ]
    
    # Create rows where Significant = 1 (for Freq count)
    if (row$Freq > 0) {
      sig_rows <- data.frame(
        Filter = rep(row$Filter, row$Freq),
        Type = rep(row$Type, row$Freq),
        Org = rep(row$Org, row$Freq),
        Significant = rep(1, row$Freq)
      )
      expanded_table <- rbind(expanded_table, sig_rows)
    }
    
    # Create rows where Significant = 0 (for Non_Counts count)
    non_sig_count <- row$Total - row$Freq
    if (non_sig_count > 0) {
      non_sig_rows <- data.frame(
        Filter = rep(row$Filter, non_sig_count),
        Type = rep(row$Type, non_sig_count),
        Org = rep(row$Org, non_sig_count),
        Significant = rep(0, non_sig_count)
      )
      expanded_table <- rbind(expanded_table, non_sig_rows)
    }
  }
  
  return(expanded_table)
}

variable_names <- list(
  "WT" = expression(bolditalic("Zic2")^bolditalic("+/+")),
  "HET" = expression(bolditalic("Zic2")^bolditalic("Ku/+"))
)

variable_labeller <- function(variable,value){return(variable_names[value])}

back_names <- list(
  "C3H" = "C3H/HeH",
  "C57BL6" = "C57BL/6N"
)

back_labeller <- function(variable,value){return(back_names[value])}



back_names_v2 <- list(
  "C3H" = "C3H/HeH",
  "F1"= "C3H/HeH:C57BL6/N F1",
  "C57BL6" = "C57BL/6N"
)

back_labeller_v2 <- function(variable,value){return(back_names_v2[value])}


#This is the only way to call to make it work!
inter_names <- list(
  "WT.C3H" = expression(bolditalic("Zic2")^bolditalic("+/+")~bold("C3H/HeH")),
  "WT.C57BL6" = expression(bolditalic("Zic2")^bolditalic("+/+")~bold("C57BL6/N")),
  "HET.C3H" = expression(bolditalic("Zic2")^bolditalic("Ku/+")~bold("C3H/HeH")),
  "HET.C57BL6" = expression(bolditalic("Zic2")^bolditalic("Ku/+")~bold("C57BL6/N")) 
  
)

inter_names_v2 <- list(
  "C3H.WT" = expression(bolditalic("Zic2")^bolditalic("+/+")~bold("C3H/HeH")),
  "C57BL6.WT" = expression(bolditalic("Zic2")^bolditalic("+/+")~bold("C57BL/6N")),
  "C3H.HET" = expression(bolditalic("Zic2")^bolditalic("Ku/+")~bold("C3H/HeH")),
  "C57BL6.HET" = expression(bolditalic("Zic2")^bolditalic("Ku/+")~bold("C57BL//6N")) 
  
)


inter_names_v3 <- list(
  "C3HHEH.WT" = expression(bolditalic("Zic2")^bolditalic("+/+")~bold("C3H/HeH")),
  "C57BL6N.WT" = expression(bolditalic("Zic2")^bolditalic("+/+")~bold("C57BL/6N")),
  "C3HHEH.HET" = expression(bolditalic("Zic2")^bolditalic("Ku/+")~bold("C3H/HeH")),
  "C57BL6N.HET" = expression(bolditalic("Zic2")^bolditalic("Ku/+")~bold("C57BL/6N")) 
  
)

inter_labeller <- function(variable,value){return(inter_names[value])}



shapviz.catboost.Model <- function(object, X_pred, X = X_pred, collapse = NULL, ...) {
  if (!inherits(X_pred, "catboost.Pool")) {
    X_pred <- catboost.load_pool(X_pred)
  }
  S <- catboost.get_feature_importance(object, X_pred, type = "ShapValues", ...)
  pp <- ncol(X_pred) + 1
  baseline <- S[1, pp]
  S <- S[, -pp, drop = FALSE]
  colnames(S) <- colnames(X_pred)
  shapviz(S, X = X, baseline = baseline, collapse = collapse)
}


```

## R Markdown

# Data Prep

```{r cars}

# load label information
label_info <- read_csv("E14_5_atlas_v24_43_label_info_v5.csv")

# load data for primary and secondary (v2) dataset
#rad_info <- prep_data("radiomics_data.csv", "240708_full_staging.csv")


rad_info <- prep_data("training_data.csv", "240708_full_staging.csv")

rad_info <- rad_info[,-2]

#I need the C3Hs from the primary dataset. 

C3Hs <- rad_info %>% filter(Background=="C3H")

# cohort 3 for secondary data validation
#rad_info_v2 <- prep_data("radiomics_data_cohort_3.csv", "240708_full_staging.csv")

rad_info_v2 <- prep_data("test_data.csv", "240708_full_staging.csv")

rad_info_v2 <- rad_info_v2[,-2]

# Identify the common columns between the two datasets
common_cols <- intersect(names(rad_info_v2), names(C3Hs))


rad_info <- rad_info %>% dplyr::select(common_cols)

#rad_info_v3 <- bind_rows(
#  dplyr::select(rad_info_v2, common_cols),
#  dplyr::select(rad_info, common_cols)
#) %>%  dplyr::filter(!(vol %in% c('231007_C3H_Ku146_e3_wt', '231106_B6_Ku_88_e1_het')))

# Select only the common columns from both datasets and bind rows
rad_info_v2 <- bind_rows(
  dplyr::select(rad_info_v2, common_cols),
  dplyr::select(C3Hs, common_cols)
) %>%  dplyr::filter(!(vol %in% c('231007_C3H_Ku146_e3_wt', '231106_B6_Ku_88_e1_het')))


rad_info <- fix_column_labels(rad_info) %>% select(where(~ !any(is.na(.))))

print(rad_info)
  
rad_info <- rad_info[, !(!(str_detect(colnames(rad_info), "shape")) & 
                          str_detect(colnames(rad_info), "ventricle|cavity|vesicle"))]
  
print(rad_info)
  

rad_info_v2 <- fix_column_labels(rad_info_v2) %>% select(where(~ !any(is.na(.))))


#rad_info_v3 <- fix_column_labels(rad_info_v3)

```
## Full penetrance plotting for genotype, background and interaction effects
```{r}

# NOTE, this data is reproducible but heavy on memory - be careful using this function
end_col <- ncol(rad_info)-5

# Determine the number of cores to use
num_cores <- detectCores()/2 - 8  # Use one less than the total number of cores

# Run the function in parallel using pblapply
g_by_e_pvals <- pblapply(rad_info[, 2:end_col], function(data) {
  g_by_e_lm(data, rad_info, pair_test = F)
}, cl = num_cores)


#split_into_chunks <- function(df, chunk_size) {
#  split(seq_len(ncol(df)), ceiling(seq_along(seq_len(ncol(df))) / chunk_size))
#}

# Number of columns to process at once (adjust chunk_size based on memory limits)
#chunk_size <- 50 # You can adjust this based on your memory constraints

# Split the rad_info dataframe into chunks
#chunks <- split_into_chunks(rad_info[, 2:end_col], chunk_size)

# Initialize an empty list to store results
#g_by_e_pvals_list <- list()

# Process each chunk using pblapply
#for (i in seq_along(chunks)) {
#  chunk <- rad_info[, chunks[[i]], drop = FALSE]
  
  # Apply the g_by_e_lm function to the chunk
#  g_by_e_pvals_chunk <- pblapply(chunk, function(data) {
#    g_by_e_lm(data, rad_info, pair_test = F)
#  }, cl = num_cores)
  
  # Store the result
#  g_by_e_pvals_list[[i]] <- g_by_e_pvals_chunk
#}

#g_by_e_pvals <- do.call(c, g_by_e_pvals_list)


g_by_e_pvals_df <- do.call(cbind, lapply(g_by_e_pvals, function(mat) {
  mat$pvals
}))

g_by_e_tvals_df <- do.call(cbind, lapply(g_by_e_pvals, function(mat) {
  mat$tvals
}))



g_by_e_pvals_df  <- relabel_df(g_by_e_pvals_df, g_by_e_pvals)

g_by_e_tvals_df  <- relabel_df(g_by_e_tvals_df, g_by_e_pvals)



fwrite(g_by_e_pvals_df, "g_by_e_pvals_df.csv", row.names=T, col.names=T)


fwrite(g_by_e_tvals_df, "g_by_e_tvals_df.csv", row.names=T, col.names=T)

g_by_e_qvals <- t(apply(g_by_e_pvals_df, 1, function(x)  p.adjust(x, method='BH')))

geno_fully_pene_feats <- g_by_e_qvals[2, ][is.numeric(g_by_e_qvals[2, ]) & !is.na(g_by_e_qvals[2, ]) & (g_by_e_qvals[2, ] < 0.05)]

back_fully_pene_feats <- g_by_e_qvals[3, ][is.numeric(g_by_e_qvals[3, ]) & !is.na(g_by_e_qvals[3, ]) & (g_by_e_qvals[3, ] < 0.05)]

int_fully_pene_feats <- g_by_e_qvals[5, ][is.numeric(g_by_e_qvals[5, ]) & !is.na(g_by_e_qvals[5, ]) & (g_by_e_qvals[5, ] < 0.05)]



```

# with 0.05 cut-off

```{r, fig.width=11, fig.height=5.25}

# plot full penetrance stuff:


plot_fully_pene_feats <- function(tvals, signif_feats){
  
  signif_tvals <-tvals[names(tvals) %in% names(signif_feats)]
  
  cluster_df <- create_cluster_df(signif_tvals)
  
  non_sign_feats$Tvals <- tvals
  
  cluster_df$Tvals <- signif_tvals
  
  
  pos_or_neg <- ifelse(signif_tvals < 0, "Negative", "Positive")
  
  cluster_df$Correlation <- pos_or_neg
  
  split_by_corr <- split(cluster_df, cluster_df$Correlation)
  
   # Check if split_by_corr$Positive is empty
  is_positive_empty <- is.null(split_by_corr$Positive) || nrow(split_by_corr$Positive) == 0
  
  # Check if split_by_corr$Negative is NULL or empty
  is_negative_empty <- is.null(split_by_corr$Negative) || nrow(split_by_corr$Negative) == 0
  
  
  if (nrow(cluster_df)>0){
    black_dots <- anti_join(non_sign_feats, cluster_df)
    plot <- ggplot(mapping=aes(x = Type, y = Tvals, col=Correlation)) +
      #geom_point(data=all_df, width = 0.5, position = position_dodge(width = 0.75), alpha=0.5)+
      #geom_point(data = split_by_corr$Positive, width = 0.5, position = position_dodge(width = 0.75)) +
      labs(x = "Feature Type", 
           y = expression("t-statistic"), color = "Association of Feature") +
      theme_minimal()+
      geom_point(data = black_dots, width = 0.5, position = position_dodge(width = 0.75), col="black")+
      theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1), legend.position = "none")
     if (!is_negative_empty){
      plot <- plot + 
      geom_point(data = split_by_corr$Negative, width = 0.5, position = position_dodge(width = 0.75))+ 
      stat_summary(data = split_by_corr$Negative, fun.data = n_fun_neg, geom = "text", col="blue", vjust = 2)
    }
    if (!is_positive_empty){ 
      plot <- plot+
      geom_point(data = split_by_corr$Positive, width = 0.5, position = position_dodge(width = 0.75))+
      stat_summary(data = split_by_corr$Positive, fun.data = n_fun_pos, geom = "text", col="red", vjust = -1)
    }
    
    
    plot <- plot +
      facet_wrap(~Org, scales = "fixed", ncol = 5)+
      theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1), legend.position = "bottom") +
      #scale_y_continuous(breaks = c(0, 1, 2, 3, 4, 5, 6, 7, 8)) +
      #facet_zoom(ylim = c(0, 2), zoom.data = ifelse((VolMean <= 2), NA, FALSE)) +
      #scale_color_manual(values = c("blue", "red"))+
      scale_color_manual(values = c("Negative"="blue", "Positive"="red"))
    
    if (!is_positive_empty & !is_negative_empty){
      plot <- plot + scale_y_continuous(limits=c(min(split_by_corr$Negative$Tvals)-3,max(split_by_corr$Positive$Tvals)+3))+
        theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1), legend.position = "none")
    } else if (!is_negative_empty){ 
      plot <- plot + scale_y_continuous(limits=c(-8,8))+
        theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1), legend.position = "none")
      }
    
  } else {
      print("wrong IF")
      n_fun_zero_pos <- function(x){return(data.frame(y = max(x), label = 0))}
      n_fun_zero_neg <- function(x){return(data.frame(y = min(x), label = 0))}
      plot <- ggplot(data=non_sign_feats, mapping=aes(x = Type, y = Tvals)) +
      #geom_point(data=all_df, width = 0.5, position = position_dodge(width = 0.75), alpha=0.5)+
      #geom_point(data = split_by_corr$Positive, width = 0.5, position = position_dodge(width = 0.75)) +
      labs(x = "Feature Type", 
           y = expression("t-statistic")) +
      theme_minimal()+
      geom_point(data = non_sign_feats, width = 0.5, position = position_dodge(width = 0.75), col="black") +
      #stat_summary(data = non_sign_feats, fun.data = n_fun_zero_pos, geom = "text", col="black", vjust = 2)+
      #stat_summary(data = split_by_corr$Positive, fun.data = n_fun_zero_neg, geom = "text", col="black", vjust = -1)+
      facet_wrap(~Org, scales = "fixed", ncol = 5)+
      theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1), legend.position = "none") +
      scale_y_continuous(limits=c(min(non_sign_feats$Tvals)-3,max(non_sign_feats$Tvals)+3))
      }
  
  #geom_segment(aes(x = "Org1_TypeB", xend = "Org2_TypeA", y = -Inf, yend = Inf), linetype = "dashed") 
  #scale_color_manual(values = type_colors)
  #facet_zoom(ylim = c(0, 2), zoom.data = ifelse((VolMean <= 2)&(Org == 'forebrain anteroventral region'), NA, FALSE))+
  
   
  #geom_point(data = split_by_corr$Negative, width = 0.5, position = position_dodge(width = 0.75))+
   
  
  print(plot)
}

non_sign_feats <- create_cluster_df(g_by_e_tvals_df[1,])

plot_fully_pene_feats(g_by_e_tvals_df[2,], geno_fully_pene_feats)
  
plot_fully_pene_feats(g_by_e_tvals_df[3,], back_fully_pene_feats)


plot_fully_pene_feats(g_by_e_tvals_df[5,], int_fully_pene_feats)

#create it as a percentage:

```

```{r, fig.width=40, fig.height=20}

plot_fully_pene_feats_as_percentages <-function(tvals, signif_feats){
  
  signif_tvals <-tvals[names(tvals) %in% names(signif_feats)]
  
  if(length(signif_tvals)==0){
    
    signif_df_counts <- table(non_sign_feats$Filter, non_sign_feats$Type, non_sign_feats$Org, useNA = "ifany") %>% as.data.frame() %>% filter(Freq>0) %>% mutate(Freq=0)
    
  } else{
    signif_df <- create_cluster_df(signif_tvals)
    signif_df_counts <- table(signif_df$Filter, signif_df$Type, signif_df$Org, useNA = "ifany") %>% as.data.frame()
  }
  
  
  all_df_counts <- table(non_sign_feats$Filter, non_sign_feats$Type, non_sign_feats$Org, useNA = "ifany") %>% as.data.frame() %>% filter(Freq>0)
  
  colnames(signif_df_counts) <- c("Filter", "Type", "Org", "Freq")

  colnames(all_df_counts) <- c("Filter", "Type", "Org", "Total")

  counts_table <- merge(signif_df_counts, all_df_counts, all.x=F, all.y=T, by=c("Filter", "Type","Org"))
  
  counts_table[is.na(counts_table)] <- 0
  
  counts_table <- counts_table %>% mutate(Prop=Freq/Total)
  
  # compute mean and standard error of the mean by subgroup
  summary_stat <- summarySE(counts_table,
  measurevar = "Prop",
  groupvars = c("Type", "Org")
  )
  # plot mean and standard error of the mean
  ggplot(subset(summary_stat, !is.na(Org)), # remove NA level for Type
         aes(x = Org, y = Prop, fill=Type))+
    geom_col() +
    geom_errorbar(aes(ymin = Prop - se, ymax = Prop + se), # add error bars
    width = 0.1 # width of error bars
    ) +
    scale_y_continuous(limits=c(0,1))+
    labs(y = "Proportion of Features", x="Organ")+
    facet_wrap(~Type, ncol = 1)+
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1), 
          legend.position = "none")
  
  # compute mean and standard error of the mean by subgroup
  summary_stat <- summarySE(counts_table,
  measurevar = "Prop",
  groupvars = c("Filter", "Org", "Type")
  )
  # plot mean and standard error of the mean
  ggplot(subset(summary_stat, !is.na(Org)), # remove NA level for Type
         aes(x = Org, y = Prop, fill=Type))+
    geom_col() +
    geom_errorbar(aes(ymin = Prop - se, ymax = Prop + se), # add error bars
    width = 0.1 # width of error bars
    ) +
    scale_y_continuous(limits=c(0,1))+
    labs(y = "Proportion of Features", x="Organ")+
    facet_wrap(~Type*Filter, ncol = 14)+
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1), 
          legend.position = "none")
  
}

stats_per_type<- function(tvals, signif_feats){
  signif_tvals <-tvals[names(tvals) %in% names(signif_feats)]
  
  if(length(signif_tvals)==0){
    
    signif_df_counts <- table(non_sign_feats$Filter, non_sign_feats$Type, non_sign_feats$Org, useNA = "ifany") %>% as.data.frame() %>% filter(Freq>0) %>% mutate(Freq=0)
    
  } else{
    signif_df <- create_cluster_df(signif_tvals)
    signif_df_counts <- table(signif_df$Filter, signif_df$Type, signif_df$Org, useNA = "ifany") %>% as.data.frame()
  }
  
  
  all_df_counts <- table(non_sign_feats$Filter, non_sign_feats$Type, non_sign_feats$Org, useNA = "ifany") %>% as.data.frame() %>% filter(Freq>0)
  
  colnames(signif_df_counts) <- c("Filter", "Type", "Org", "Freq")

  colnames(all_df_counts) <- c("Filter", "Type", "Org", "Total")

  counts_table <- merge(signif_df_counts, all_df_counts, all.x=F, all.y=T, by=c("Filter", "Type","Org"))
  
  counts_table[is.na(counts_table)] <- 0
  
  counts_table <- counts_table %>% mutate(Non_Counts=Total-Freq)

  
  table_per_type <- split(counts_table, counts_table$Type)
  
  pvals_per_type <- lapply(table_per_type, function(table){
    
    #table <- table %>% group_by(Org)
    table_summary <- aggregate(cbind(Freq, Non_Counts) ~ Org, data = table, FUN = mean)
    
    contingency_table <- as.matrix(table_summary[, c("Freq", "Non_Counts")])
  
    fisher_test <- fisher.test(contingency_table, simulate.p.value=TRUE)
  
    return(fisher_test$p.value)
  })
  
  
  mean_filt_table <- aggregate(cbind(Freq, Non_Counts) ~ Type*Org, data = counts_table, FUN = mean)
  
  is_type_sign_table <- aggregate(cbind(Freq, Non_Counts) ~ Type, data = mean_filt_table, FUN = sum)
  
  
  print(fisher.test(as.matrix(is_type_sign_table[, c("Freq", "Non_Counts")]),simulate.p.value=TRUE))
  
  
  is_org_sign_table <- aggregate(cbind(Freq, Non_Counts) ~ Org, data = mean_filt_table, FUN = sum)
  
  
  print(fisher.test(as.matrix(is_org_sign_table[, c("Freq", "Non_Counts")]),simulate.p.value=TRUE))
  
  
  
  qvals <-p.adjust(pvals_per_type, method='BH')
  
  print(qvals)
  
  sign_tables <- table_per_type[qvals < 0.05]
  
  test <- lapply(sign_tables, function(table){
    
    p_matrix <- pairwise_fisher(table)
    #p_values <- p_matrix[upper.tri(p_matrix, diag = FALSE)]  # Extract upper triangle p-values
    #p_adj <- p.adjust(p_values, method = "bonferroni")             # Adjust p-values
    
    # Insert the adjusted p-values back into the matrix
    #p_matrix[upper.tri(p_matrix, diag = FALSE)] <- p_adj
    #p_matrix[lower.tri(p_matrix, diag = FALSE)] <- p_adj     # Reflect adjusted p-values to lower triangle
    
    # Use `multcompLetters` to generate the compact letter display (CLD)
    cld_result <- multcompLetters(p_matrix, threshold =0.05, compare = "<")
    
  
    
    print(cld_result)

    
  })
  
  
}

non_sign_feats <- create_cluster_df(g_by_e_tvals_df[1,])

plot_fully_pene_feats_as_percentages(g_by_e_tvals_df[2,], geno_fully_pene_feats)

plot_fully_pene_feats_as_percentages(g_by_e_tvals_df[3,], back_fully_pene_feats)

plot_fully_pene_feats_as_percentages(g_by_e_tvals_df[5,], int_fully_pene_feats)

stats_per_type(g_by_e_tvals_df[3,], back_fully_pene_feats)

stats_per_type(g_by_e_tvals_df[2,], geno_fully_pene_feats)



```


```{r, fig.width=14, fig.height=20}


# Define the plotting function
plot_logistic_regression <- function(tvals, signif_feats){
  signif_tvals <-tvals[names(tvals) %in% names(signif_feats)]
  
  if(length(signif_tvals)==0){
    
    signif_df_counts <- table(non_sign_feats$Filter, non_sign_feats$Type, non_sign_feats$Org, useNA = "ifany") %>% as.data.frame() %>% filter(Freq>0) %>% mutate(Freq=0)
    
  } else{
    signif_df <- create_cluster_df(signif_tvals)
    signif_df_counts <- table(signif_df$Filter, signif_df$Type, signif_df$Org, useNA = "ifany") %>% as.data.frame()
  }
  
  
  all_df_counts <- table(non_sign_feats$Filter, non_sign_feats$Type, non_sign_feats$Org, useNA = "ifany") %>% as.data.frame() %>% filter(Freq>0)
  
  colnames(signif_df_counts) <- c("Filter", "Type", "Org", "Freq")

  colnames(all_df_counts) <- c("Filter", "Type", "Org", "Total")

  counts_table <- merge(signif_df_counts, all_df_counts, all.x=F, all.y=T, by=c("Filter", "Type","Org"))
  
  counts_table[is.na(counts_table)] <- 0
  
  
  counts_table <- expand_counts_table(counts_table)
  
  
  
  #counts_table[is.na(counts_table)] <- 0
  
  
  #counts_table <- expand_counts_table(counts_table)
  
  #So for filter - the orginal filter should be the baseline:
  
 
  
  counts_table$Filter <- factor(counts_table$Filter, levels = c("original", setdiff(levels(counts_table$Filter), "original")))

  counts_table$Type <- factor(counts_table$Type, levels = c("shape", setdiff(levels(counts_table$Type), "shape")))
  
  #counts_table$Org <- factor(counts_table$Org, levels = c("forebrain between lateral ventricles", setdiff(levels(counts_table$Org), "forebrain between lateral ventricles")))
  
  
  #counts_table <- counts_table %>% mutate_all(funs(str_replace_all(., " ", "_")))
  
  
  # List of variables to calculate counts for
  variables <- c("Type", "Org", "Filter")
  # Loop through each variable
  
  for (var in variables) {
    # Print the name of the variable
    cat("\nNumber of observations for each level of", var, ":\n")
    # Group by the variable and count observations
    counts <- counts_table %>% dplyr::group_by(!!sym(var))
    print(counts)
    counts <- counts_table %>% dplyr::group_by(!!sym(var)) %>% dplyr::summarise(n = dplyr::n(), .groups = "drop")
    # Print the result
    print(counts)
    }
  
  
  # Step 1: Fit logistic regression model, -1 removes the intercept, this sets the baseline to 0 in the model. 
  
  # Convert data to a model matrix with all main effects and interactions
  #x <- model.matrix(Significant ~ Org * Type * Filter, data = counts_table)  # -1 to exclude intercept
  #y <- counts_table$Significant  # Response variable
  
  # Assuming X is the design matrix and y is the binary response variable
  #model <- debiased.glmnet(X, y, family = "binomial")
  #print(summary(model))
  
  
  
  # Fit LASSO model with cross-validation to find optimal lambda
  #lasso_model <- cv.glmnet(x, y, family = "binomial", alpha = 1)  # alpha = 1 for LASSO
  #best_lambda <- lasso_model$lambda.min  # Optimal lambda
  
  
  
  # Get the coefficients at the best lambda (optimal regularization)
  #selected_coefs <- coef(lasso_model, s = best_lambda)
  
  # Filter out the zero coefficients
  #selected_coefs_matrix <- as.matrix(selected_coefs)
  #selected_terms <- rownames(selected_coefs_matrix)[selected_coefs_matrix != 0]
  #selected_terms <- selected_terms[selected_terms != "(Intercept)"]  # Exclude intercept if present
  
  
  #cat("\n Selected Terms \n")
  #print(selected_terms)
  
  
  #cat("\n Summary of model \n")
  
  #selected_formula <- as.formula(paste("Significant ~", paste(selected_terms, collapse = " + ")))
  
  #print(selected_formula)

  
  # Fit the logistic regression model with only the selected terms
  
  model <- glm(Significant~Type + Org + Filter, family="binomial",
               data = counts_table, na.action = na.fail)
  
  #model2 <- glm(Significant~Type:Org + Org:Filter + Type:Filter + Type + Org + Filter, 
  #              data = counts_table, family = binomial)
  
  
  #print(check_collinearity(model))
  
  print(check_model(model))
  
  
  #print(anova(model2, model, test = "Chisq"))
  
  results_table <- as.data.frame(coef(summary(model)))
  
  results_table$`Pr(>|z|)` <- p.adjust(results_table$`Pr(>|z|)`, method = "BH")
  
  
  #results_table <-results_table %>% filter(`Pr(>|z|)` < 0.05)
  
  print(results_table)
  
  options(na.action = "na.fail")
  
  model_selection <- dredge(model)
  # View model selection results
  summary(model_selection)
  
  best_models <- get.models(model_selection, subset = delta < 2)  # Select models within 2 AIC units

  # Extract and display p-values from the selected models
  for (i in seq_along(best_models)) {
    cat("Model", i, "p-values:\n")
    good_results <- as.data.frame(coef(summary(best_models[[i]])))
    cat("\n")
  }
  
  
  
  print(check_model(best_models[[1]]))
  
  good_results$`Pr(>|z|)` <- p.adjust(good_results$`Pr(>|z|)`, method = "BH")
  
  good_results <- good_results %>% filter(`Pr(>|z|)` < 0.05)
  
  print(good_results)
  
  
  
  
  print(length(good_results[good_results < 0.05]))

  # View model selection results
  #summary(model_selection)
  
  options(na.action = "na.omit")
  # Step 2: Get predicted probabilities with confidence intervals
  emm <- emmeans(model, ~Type + Org + Filter, type = "response")
  emm_df <- as.data.frame(emm)
  
  
  
  
  # empty rows give stupid CIs
  emm_df <- emm_df %>% filter(prob > 0.01)
  
  # Step 3: Plot predicted probabilities with confidence intervals
  plot <- ggplot(emm_df, aes(x = Org, y = prob, color = Type)) +
    geom_point(size = 3, position = position_dodge(width = 0.5)) +
    geom_errorbar(aes(ymin = asymp.LCL, ymax = asymp.UCL), 
                  width = 0.2, position = position_dodge(width = 0.5)) +
    labs(
      title = "Predicted Probabilities of Significant Features by Type, Filter and Org",
      x = "Org",
      y = "Predicted Probability",
      color = "Type"
    ) +
    theme_minimal() +
    facet_wrap(~Filter, ncol=3)+
    theme(
      plot.title = element_text(hjust = 0.5, size = 16),
      axis.text.x = element_text(angle = 90, hjust = 1),
      legend.position = "top"
    )
  
  return(plot)
}

non_sign_feats <- create_cluster_df(g_by_e_tvals_df[1,])

plot_logistic_regression(g_by_e_tvals_df[3,], back_fully_pene_feats)

plot_logistic_regression(g_by_e_tvals_df[2,], geno_fully_pene_feats)


#non_sign_feats <- create_cluster_df(g_by_e_tvals_df_v2[1,])

#plot_logistic_regression(g_by_e_tvals_df_v2[3,], back_fully_pene_feats_v2)

#plot_logistic_regression(g_by_e_tvals_df_v2[2,], geno_fully_pene_feats_v2)


```

```{r, fig.width=8, fig.height=8}

plot_poisson_regression <- function(tvals, signif_feats){
  signif_tvals <-tvals[names(tvals) %in% names(signif_feats)]
  
  if(length(signif_tvals)==0){
    
    signif_df_counts <- table(non_sign_feats$Filter, non_sign_feats$Type, non_sign_feats$Org, useNA = "ifany") %>% as.data.frame() %>% filter(Freq>0) %>% mutate(Freq=0)
    
  } else{
    signif_df <- create_cluster_df(signif_tvals)
    signif_df_counts <- table(signif_df$Filter, signif_df$Type, signif_df$Org, useNA = "ifany") %>% as.data.frame()
  }
  
  
  all_df_counts <- table(non_sign_feats$Filter, non_sign_feats$Type, non_sign_feats$Org, useNA = "ifany") %>% as.data.frame() %>% filter(Freq>0)
  
  colnames(signif_df_counts) <- c("Filter", "Type", "Org", "Freq")

  colnames(all_df_counts) <- c("Filter", "Type", "Org", "Total")

  counts_table <- merge(signif_df_counts, all_df_counts, all.x=F, all.y=T, by=c("Filter", "Type","Org"))
  
  counts_table[is.na(counts_table)] <- 0
  
  
  # perform poisson regression:

  # Proceed with setting the baseline levels
  counts_table$Filter <- factor(counts_table$Filter, levels = c("original", setdiff(levels(counts_table$Filter), "original")))
  counts_table$Type <- factor(counts_table$Type, levels = c("shape", setdiff(levels(counts_table$Type), "shape")))
  counts_table$Org <- factor(counts_table$Org, levels = c("pons", setdiff(levels(counts_table$Org), "pons")))
  
  #counts_table <- counts_table %>% filter(Type!="shape")
  
  #model_poisson <- glm(Freq ~ Type+Filter+Org, family = poisson(link = "log"), offset = log(Total), data = counts_table)
  print(counts_table)
  library(pscl)
  model_poisson <- glm(Freq ~ Type+Filter+Org + offset(log(Total)), data= counts_table, family=quasipoisson(link = "log"))
  
  print(summary(model_poisson))
  #model_poisson <- stepAIC(model_poisson, direction = "both")

  # View the model summary
  print(hist(counts_table$Freq))
  print(check_collinearity(model_poisson))
  
  print(check_model(model_poisson, residual_type = "normal"))
  #print(summary(model_poisson))
  
  print(coef(summary(model_poisson)))
  
  #pois_results <- as.data.frame(coef(summary(model_poisson))) %>% filter(`Pr(>|z|)` < 0.05)
  
  #print(pois_results)
  
  
  #ld.vars <- attributes(alias(model_poisson)$Complete)$dimnames[[1]]
  
  #print(ld.vars)
  #print(vif(model_poisson))
  
  
  
  #print(penis)
  
  pois_results <- as.data.frame(coef(summary(model_poisson))$count) %>% filter(`Pr(>|z|)` < 0.05)
  
  #print(pois_results)
  
 
  return(pois_results)
}


plot_poisson_regression(g_by_e_tvals_df[3,], back_fully_pene_feats)

plot_poisson_regression(g_by_e_tvals_df[2,], geno_fully_pene_feats)

```

```{r, fig.width=9, fig.height=4.5}

plot_per_filt_type <- function(tvals, signif_feats) {
  
  # Prepare the data, similar to the `plot_fully_pene_feats_as_percentages` function
  signif_tvals <- tvals[names(tvals) %in% names(signif_feats)]
  
  if (length(signif_tvals) == 0) {
    signif_df_counts <- table(non_sign_feats$Filter, non_sign_feats$Type, non_sign_feats$Org, useNA = "ifany") %>% 
      as.data.frame() %>% filter(Freq > 0) %>% mutate(Freq = 0)
  } else {
    signif_df <- create_cluster_df(signif_tvals)
    signif_df_counts <- table(signif_df$Filter, signif_df$Type, signif_df$Org, useNA = "ifany") %>% as.data.frame()
  }
  
  all_df_counts <- table(non_sign_feats$Filter, non_sign_feats$Type, non_sign_feats$Org, useNA = "ifany") %>% 
    as.data.frame() %>% filter(Freq > 0)
  
  colnames(signif_df_counts) <- c("Filter", "Type", "Org", "Freq")
  colnames(all_df_counts) <- c("Filter", "Type", "Org", "Total")
  
  counts_table <- merge(signif_df_counts, all_df_counts, all.x = FALSE, all.y = TRUE, by = c("Filter", "Type", "Org"))
  counts_table[is.na(counts_table)] <- 0
  counts_table <- counts_table %>% mutate(Prop = Freq / Total, Non_Counts = Total - Freq)
  
  # Compute mean and standard error of the mean by subgroup
  summary_stat <- summarySE(counts_table, measurevar = "Prop", groupvars = c("Filter", "Type", "Org"))
  
  # Create the plot using facet_grid
  plot <- ggplot(subset(summary_stat, !is.na(Org)), aes(x = Org, y = Prop, fill = Type)) +
    geom_col() +
    geom_errorbar(aes(ymin = Prop - se, ymax = Prop + se), width = 0.1) +
    scale_y_continuous(limits = c(0, 1)) +
    labs(y = "Proportion of Features", x = "Organ") +
    facet_grid(Type ~ Filter) +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1), legend.position = "none")
  
  # Calculate partial Fisher squares and perform tests
  
  fisher_results <- lapply(split(counts_table, list(counts_table$Type, counts_table$Filter)), function(sub_table) {
    if (nrow(sub_table) == 0) {
    message("No data for summary statistics. Returning empty p-value")
    return(NA)
  }
    table_summary <- aggregate(cbind(Freq, Non_Counts) ~ Org, data = sub_table, FUN = sum)
    if (sum(table_summary$Freq) ==0){
      return(1)
    }
    contingency_table <- as.matrix(table_summary[, c("Freq", "Non_Counts")])
    print(contingency_table)
    fisher_test <- fisher.test(contingency_table, simulate.p.value = TRUE)
    return(fisher_test$p.value)
  })
  
  # Convert the list of p-values into a data frame for heatmap visualization
  fisher_pvals_df <- do.call(rbind, lapply(names(fisher_results), function(name) {
    split_name <- strsplit(name, "\\.")[[1]]
    data.frame(Type = split_name[1], Filter = split_name[2], P_Value = fisher_results[[name]])
  }))
  
  fisher_pvals_df$Adj_P_Value <- p.adjust(fisher_pvals_df$P_Value, method = "BH")
  
  # Create a 2D heatmap of p-values
  heatmap <- ggplot(fisher_pvals_df, aes(x = Filter, y = Type, fill = -log10(Adj_P_Value))) +
    geom_tile() +
    scale_fill_viridis_c(
    option = "inferno",
    values = scales::rescale(c(0, 1.75, 2, 3.25)),
    limits = c(0, 4)) +
     labs(title = "Heatmap of Fisher Test P-Values", x = "Filter", y = "Type", fill = "-log10(P.value)")  +
    theme_minimal()+
    theme(legend.position = "bottom", axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
  
  # Print the plot and heatmap
  print(plot)
  print(heatmap)
}

non_sign_feats <- create_cluster_df(g_by_e_tvals_df[1,])
plot_per_filt_type(g_by_e_tvals_df[3,], back_fully_pene_feats)
plot_per_filt_type(g_by_e_tvals_df[2,], geno_fully_pene_feats)

#non_sign_feats <- create_cluster_df(g_by_e_tvals_df_v2[1,])
#plot_per_filt_type(g_by_e_tvals_df_v2[3,], back_fully_pene_feats_v2)
#plot_per_filt_type(g_by_e_tvals_df_v2[2,], geno_fully_pene_feats_v2)

#non_sign_feats <- create_cluster_df(g_by_e_tvals_df_v3[1,])
#plot_per_filt_type(g_by_e_tvals_df_v3[3,], back_fully_pene_feats_v3)

```


```{r}

logistic_regression_analysis <- function(tvals, signif_feats){
  signif_tvals <-tvals[names(tvals) %in% names(signif_feats)]
  
  if(length(signif_tvals)==0){
    
    signif_df_counts <- table(non_sign_feats$Filter, non_sign_feats$Type, non_sign_feats$Org, useNA = "ifany") %>% as.data.frame() %>% filter(Freq>0) %>% mutate(Freq=0)
    
  } else{
    signif_df <- create_cluster_df(signif_tvals)
    signif_df_counts <- table(signif_df$Filter, signif_df$Type, signif_df$Org, useNA = "ifany") %>% as.data.frame()
  }
  
  
  all_df_counts <- table(non_sign_feats$Filter, non_sign_feats$Type, non_sign_feats$Org, useNA = "ifany") %>% as.data.frame() %>% filter(Freq>0)
  
  colnames(signif_df_counts) <- c("Filter", "Type", "Org", "Freq")

  colnames(all_df_counts) <- c("Filter", "Type", "Org", "Total")

  counts_table <- merge(signif_df_counts, all_df_counts, all.x=F, all.y=T, by=c("Filter", "Type","Org"))
  
  counts_table[is.na(counts_table)] <- 0
  
  
  counts_table <- expand_counts_table(counts_table)
  
  #So for filter - the orginal filter should be the baseline:
  
  counts_table$Filter <- factor(counts_table$Filter, levels = c("original", setdiff(levels(counts_table$Filter), "original")))
  
  counts_table$Type <- factor(counts_table$Type, levels = c("shape", setdiff(levels(counts_table$Type), "shape")))
  
  counts_table$Org <- factor(counts_table$Org, levels = c("forebrain between lateral ventricles", setdiff(levels(counts_table$Org), "forebrain between lateral ventricles")))
  
  model <- glm(Significant ~ Org*Type*Filter, data = counts_table, family = binomial)
  cat("Logistic Regression Model Summary:\n")
  print(summary(model))
  
  
  # Step 4: Odds Ratios with 95% Confidence Intervals
  cat("\nOdds Ratios and 95% Confidence Intervals:\n")
  odds_ratios <- exp(cbind(Odds_Ratio = coef(model), confint(model)))
  print(odds_ratios)
  
  # Step 5: Model Diagnostics
  cat("\nModel Diagnostics:\n")
  
  # Hosmer-Lemeshow goodness-of-fit test
  hoslem_test <- hoslem.test(counts_table$Significant, fitted(model))
  print(hoslem_test)
  
  # Step 6: Optional interaction analysis
  #model_interaction <- glm(Significant ~ Type * Org * Filter, data = counts_table, family = binomial)
  #cat("\nInteraction Model Summary:\n")
  #print(summary(model_interaction))
  
  base_model<- glm(Significant ~ Org+Type+Filter, data = counts_table, family = binomial)
  
  # Post-hoc tests on interaction if significant
  if (anova(base_model, model, test="Chisq")[2, "Pr(>Chi)"] < 0.05) {
    cat("\nSignificant Interaction Detected. Performing Pairwise Comparisons by Org:\n")
    interaction_pairwise <- emmeans(model, pairwise ~ Type | Org, adjust = "BH")
    print(interaction_pairwise$contrasts)
  } else {
    cat("\nNo significant interaction detected between Type and Org.\n")
  }
  
  # Return all results as a list
  return(list(
    model_summary = summary(model),
    odds_ratios = odds_ratios,
    type_pairwise = type_pairwise,
    org_pairwise = org_pairwise,
    hoslem_test = hoslem_test,
    interaction_model_summary = summary(model_interaction)
  ))
}

# Example usage:
# result <- logistic_regression_analysis(counts_table)



logistic_regression_analysis(g_by_e_tvals_df[3,], back_fully_pene_feats)

logistic_regression_analysis(g_by_e_tvals_df[2,], geno_fully_pene_feats)


```


## Full penetrance plotting for genotype, background and interaction effects
```{r, fig.width==11, fig.height=6}

#rad_info_v2 <- rad_info_v2 %>% select_if(~ !any(is.na(.)))
# get largest col 
end_col <- ncol(rad_info_v2)-5

# Determine the number of cores to use
num_cores <- detectCores()/2 - 1  # Use one less than the total number of cores

# Run the function in parallel using mclapply
g_by_e_pvals_v2 <- pblapply(rad_info_v2[, 2:end_col], function(data) {
  g_by_e_lm(data, rad_info_v2, pair_test = F)
}, cl = num_cores)



g_by_e_pvals_v2_filtered <- Filter(function(mat) {
  is.list(mat) && !is.null(mat$pvals)
}, g_by_e_pvals_v2)

g_by_e_pvals_df_v2 <- do.call(cbind, lapply(g_by_e_pvals_v2, function(mat) {
  mat$pvals
}))



g_by_e_tvals_df_v2 <- do.call(cbind, lapply(g_by_e_pvals_v2, function(mat) {
  mat$tvals
}))

g_by_e_pvals_df_v2  <- relabel_df(g_by_e_pvals_df_v2, g_by_e_pvals_v2)

g_by_e_tvals_df_v2  <- relabel_df(g_by_e_tvals_df_v2, g_by_e_pvals_v2)


fwrite(g_by_e_pvals_df_v2, "g_by_e_pvals_df_v2.csv", row.names=T, col.names=T)


fwrite(g_by_e_tvals_df_v2, "g_by_e_tvals_df_v2.csv", row.names=T, col.names=T)

g_by_e_qvals_v2 <- t(apply(g_by_e_pvals_df_v2, 1, function(x)  p.adjust(x, method='BH')))

geno_fully_pene_feats_v2 <- g_by_e_qvals_v2[2, ][g_by_e_qvals_v2[2, ] < 0.05]

back_fully_pene_feats_v2 <- g_by_e_qvals_v2[3, ][g_by_e_qvals_v2[3, ] < 0.05]

int_fully_pene_feats_v2 <- g_by_e_qvals_v2[5, ][g_by_e_qvals_v2[5, ] < 0.05]

```


```{r, fig.width=11, fig.height=4}
non_sign_feats <- create_cluster_df(g_by_e_tvals_df_v2[1,])

plot_fully_pene_feats(g_by_e_tvals_df_v2[2,], geno_fully_pene_feats_v2)
  
plot_fully_pene_feats(g_by_e_tvals_df_v2[3,], back_fully_pene_feats_v2)

plot_fully_pene_feats(g_by_e_tvals_df_v2[5,], int_fully_pene_feats_v2)


stats_per_type(g_by_e_tvals_df_v2[3,], back_fully_pene_feats_v2)

stats_per_type(g_by_e_tvals_df_v2[2,], geno_fully_pene_feats_v2)

```


```{r}

non_sign_feats <- create_cluster_df(g_by_e_tvals_df_v2[1,])

plot_logistic_regression(g_by_e_tvals_df_v2[3,], back_fully_pene_feats_v2)

plot_logistic_regression(g_by_e_tvals_df_v2[2,], geno_fully_pene_feats_v2)

```

```{r, fig.width=3, fig.height=9}

plot_fully_pene_feats_as_percentages(g_by_e_tvals_df_v2[2,], geno_fully_pene_feats_v2)

plot_fully_pene_feats_as_percentages(g_by_e_tvals_df_v2[3,], back_fully_pene_feats_v2)

plot_fully_pene_feats_as_percentages(g_by_e_tvals_df_v2[5,], int_fully_pene_feats_v2)

```

# merged dataset



```{r, fig.width==11, fig.height=6}

#rad_info_v3 <- rad_info_v3 %>% select_if(~ !any(is.na(.)))
# get largest col 
end_col <- ncol(rad_info_v3)-5

# Determine the number of cores to use
num_cores <- detectCores()/2 - 1  # Use one less than the total number of cores

# Run the function in parallel using mclapply
g_by_e_pvals_v3 <- pblapply(rad_info_v3[, 2:end_col], function(data) {
  g_by_e_lm(data, rad_info_v3, pair_test = F)
}, cl = num_cores)



g_by_e_pvals_v3_filtered <- Filter(function(mat) {
  is.list(mat) && !is.null(mat$pvals)
}, g_by_e_pvals_v3)

g_by_e_pvals_df_v3 <- do.call(cbind, lapply(g_by_e_pvals_v3, function(mat) {
  mat$pvals
}))



g_by_e_tvals_df_v3 <- do.call(cbind, lapply(g_by_e_pvals_v3, function(mat) {
  mat$tvals
}))

g_by_e_pvals_df_v3  <- relabel_df(g_by_e_pvals_df_v3, g_by_e_pvals_v3)

g_by_e_tvals_df_v3  <- relabel_df(g_by_e_tvals_df_v3, g_by_e_pvals_v3)


fwrite(g_by_e_pvals_df_v3, "g_by_e_pvals_df_v3.csv", row.names=T, col.names=T)


fwrite(g_by_e_tvals_df_v3, "g_by_e_tvals_df_v3.csv", row.names=T, col.names=T)

g_by_e_qvals_v3 <- t(apply(g_by_e_pvals_df_v3, 1, function(x)  p.adjust(x, method='BH')))

geno_fully_pene_feats_v3 <- g_by_e_qvals_v3[2, ][g_by_e_qvals_v3[2, ] < 0.05]

back_fully_pene_feats_v3 <- g_by_e_qvals_v3[3, ][g_by_e_qvals_v3[3, ] < 0.05]

int_fully_pene_feats_v3 <- g_by_e_qvals_v3[5, ][g_by_e_qvals_v3[5, ] < 0.05]

```


```{r, fig.width=11, fig.height=8}
non_sign_feats <- create_cluster_df(g_by_e_tvals_df_v3[1,])

plot_fully_pene_feats(g_by_e_tvals_df_v3[2,], geno_fully_pene_feats_v3)
  
plot_fully_pene_feats(g_by_e_tvals_df_v3[3,], back_fully_pene_feats_v3)

plot_fully_pene_feats(g_by_e_tvals_df_v3[5,], int_fully_pene_feats_v3)
```


```{r, fig.width=30, fig.height=15}

plot_fully_pene_feats_as_percentages(g_by_e_tvals_df_v3[2,], geno_fully_pene_feats_v3)

plot_fully_pene_feats_as_percentages(g_by_e_tvals_df_v3[3,], back_fully_pene_feats_v3)

plot_fully_pene_feats_as_percentages(g_by_e_tvals_df_v3[5,], int_fully_pene_feats_v3)

```
## fully pene stats pr

```{r}
non_sign_feats <- create_cluster_df(g_by_e_tvals_df_v3[1,])

plot_logistic_regression(g_by_e_tvals_df_v3[3,], back_fully_pene_feats_v3)

plot_logistic_regression(g_by_e_tvals_df_v3[2,], geno_fully_pene_feats_v3)
  

stats_per_type(g_by_e_tvals_df_v3[3,], back_fully_pene_feats_v3)

stats_per_type(g_by_e_tvals_df_v3[2,], geno_fully_pene_feats_v3)

#stats_per_type(g_by_e_tvals_df_v3[5,], int_fully_pene_feats_v3)

```


## Including Plots

You can also embed plots, for example:

```{r echo=FALSE}
# Identifies significant feats (i.e., feats with a mean-vol != 1 are significant, 
# feats ==1 were non significant in perm but were labelled as 1 as NA stuffed clustermapping)
signif_feat_finder <- function(heatmap_str, rad_info,HPE_bros, out_dir, staging_str){
  #reads heatmap and fixes first column name
  significant_feats <- read_csv(heatmap_str)
  colnames(significant_feats)[1] <- "vol"
  
  #replaces spaces with _ to match rad_info
  colnames(significant_feats) <- str_replace_all(colnames(significant_feats), " ", "_") 
  
  colnames(significant_feats) <- gsub("[0-9.]", "", colnames(significant_feats)) 
  
  # removes i) duplicated columns and ii) feats significant in any C3Hs and all wts. Can't do a perfect 1 threshold as 1 in 20 odd embryos can be significant in
  # wild-types (p<0.05) = 5% chance of false negatives
  
  significant_feats <- significant_feats %>% dplyr::select(unique(names(.)))
  
  # keep a copy before filtering
  all_feats <- significant_feats
  
  background <- significant_feats %>% filter(str_detect(vol, "wt")) %>% select_if(is.numeric)
  C3Hs <- significant_feats %>% filter(str_detect(vol, "C3H")) %>% select_if(is.numeric)
  
  cols_outside_range <- names(which(colMeans(background) < 0.95 | colMeans(background) > 1.05))
  
  cols_outside_range2 <- names(which(colMeans(C3Hs) < 0.95 |colMeans(C3Hs) > 1.05))
  
  HPE_feats <- significant_feats %>%
    filter(vol %in% HPE_bros) %>% select_if(is.numeric)
  
  bad_HPE_feats <- names(which(apply(HPE_feats, 2, function(x) any(x == 1))))
  
  good_HPE_feats <- names(which(apply(HPE_feats, 2, function(x) all(x != 1))))
  

  significant_feats <- significant_feats[,!(colnames(significant_feats) %in% c(cols_outside_range, cols_outside_range2, bad_HPE_feats))]
  
  
  significant_feats <- significant_feats[,(colnames(significant_feats) %in% c("vol", good_HPE_feats))]
  
  #write.csv(significant_feats, out_dir)
  
  filtered_dataset <- rad_info[, colnames(rad_info) %in% colnames(significant_feats)]

  filtered_dataset$vol <- rad_info$vol
  
  staging_info <- read_csv(staging_str)
  

  filtered_dataset <- merge(filtered_dataset, staging_info, by='vol')
  
  return(list(significant_feats = significant_feats, all_feats = all_feats, filtered_dataset = filtered_dataset))
    
}



sev_HPE_bros <- c("210913_b6ku_22300_e6_het",
"210913_b6ku_22300_e8_het",
"220422_BL6_Ku_50_e5_het")

HPE_bros <- c("210913_b6ku_22300_e6_het",
"210913_b6ku_22300_e8_het",
"210926_b6ku_22296_e7_het",
"210926_b6ku_22299_e1_het",
"220422_BL6_Ku_50_e5_het")

HPE_cohort_3_bros <- c('231218_B6_Ku_92_e3_het', '240321_BL6_153_e4_het', '240427_BL6_174_e2_het',
               '240404_BL6_Ku_190_e2_het', '240530_BL6_Ku_145_e1_het','240530_BL6_Ku_35_e2_het',
                 '231106_B6_Ku_88_e3_het', '240308_BL6_164_e5_het', '240530_BL6_Ku_69_e8_het',
                 '231120_B6_Ku_204_e4_het', '231218_B6_Ku_100_e1_wt', '240407_BL6_Ku_188_e5_het')

HPE_cohort_3_sev <- c('231218_B6_Ku_92_e3_het', '240321_BL6_153_e4_het', '240427_BL6_174_e2_het',
                      '240530_BL6_Ku_145_e1_het','240530_BL6_Ku_35_e2_het')

HPE_cohort_3_mild <- c('231218_B6_Ku_100_e1_wt','240308_BL6_164_e5_het', '231106_B6_Ku_88_e3_het', 
                       '240407_BL6_Ku_188_e5_het', '231120_B6_Ku_204_e4_het', '240530_BL6_Ku_69_e8_het')

HPE_cohort_3_phil <- c('231218_B6_Ku_100_e1_wt','240308_BL6_164_e5_het', '231106_B6_Ku_88_e3_het')

HPE_cohort_3_ant <- c('240530_BL6_Ku_69_e8_het','231120_B6_Ku_204_e4_het', '240407_BL6_Ku_188_e5_het',
                      '231218_B6_Ku_92_e3_het', '240321_BL6_153_e4_het', '240427_BL6_174_e2_het',
                      '240530_BL6_Ku_145_e1_het','240530_BL6_Ku_35_e2_het')

result <- signif_feat_finder("full_datasets_heatmap.csv", rad_info, HPE_bros, "significant_feats_exact.csv", "220914_full_staging.csv")

significant_feats <- result$significant_feats
all_feats <- result$all_feats
filt_dataset <- result$filtered_dataset


result_sev <- signif_feat_finder("full_datasets_heatmap.csv", rad_info, sev_HPE_bros, "significant_feats_exact_sev.csv", "220914_full_staging.csv")

all_feats_sev <- result_sev$all_feats
filt_dataset_sev <- result_sev$filtered_dataset
significant_feats_sev <- result_sev$significant_feats


result_cohort3 <- signif_feat_finder("full_datasets_heatmap_cohort_3.csv", rad_info_v2, HPE_cohort_3_mild, "significant_feats_exact_cohort_3.csv","240708_full_staging.csv")

significant_feats_c3 <- result_cohort3$significant_feats
all_feats_c3 <- result_cohort3$all_feats
filt_dataset_c3 <- result_cohort3$filtered_dataset



result_cohort3_sev <- signif_feat_finder("full_datasets_heatmap_cohort_3.csv", rad_info_v2, HPE_cohort_3_sev, "significant_feats_exact_cohort_3.csv","240708_full_staging.csv")

significant_feats_c3_sev <- result_cohort3_sev$significant_feats
all_feats_c3_sev <- result_cohort3_sev$all_feats
filt_dataset_c3_sev <- result_cohort3_sev$filtered_dataset



result_phil <- signif_feat_finder("full_datasets_heatmap_cohort_3.csv",  rad_info_v2, HPE_cohort_3_phil, "significant_feats_exact_cohort_3_phil.csv", "240708_full_staging.csv")

significant_feats_c3_phil <- result_phil$significant_feats %>%  filter(if_any(where(is.numeric), ~ . != 1))
all_feats_c3_phil <- result_phil$all_feats
filt_dataset_c3_phil <- result_phil$filtered_dataset


result_ant <- signif_feat_finder("full_datasets_heatmap_cohort_3.csv",  rad_info_v2, HPE_cohort_3_ant, "significant_feats_exact_cohort_3.csv", "240708_full_staging.csv")

significant_feats_c3_ant <- result_ant$significant_feats %>%  filter(if_any(where(is.numeric), ~ . != 1))
all_feats_c3_ant <- result_ant$all_feats
filt_dataset_c3_ant <- result_ant$filtered_dataset

```

```{r fig.width=5, fig.height=9}
non_sign_feats <- create_cluster_df(g_by_e_tvals_df_v2[1,])
#plot_fully_pene_feats_as_percentages(significant_feats_sev, all_feats_sev)
#plot_fully_pene_feats_as_percentages(significant_feats, all_feats)

#non_sign_feats <- create_cluster_df(all_feats_sev)

#plot_logistic_regression(filt_dataset_sev, significant_feats_sev)

```

```{r fig.height=5, fig.width=5}


plot_fully_pene_feats_as_percentages_just_av <-function(tvals, signif_feats){
  
  signif_tvals <-tvals[names(tvals) %in% names(signif_feats)]
  
  if(length(signif_tvals)==0){
    
    signif_df_counts <- table(non_sign_feats$Filter, non_sign_feats$Type, non_sign_feats$Org, useNA = "ifany") %>% as.data.frame() %>% filter(Freq>0) %>% mutate(Freq=0)
    
  } else{
    signif_df <- create_cluster_df(signif_tvals)
    signif_df_counts <- table(signif_df$Filter, signif_df$Type, signif_df$Org, useNA = "ifany") %>% as.data.frame()
  }
  
  
  all_df_counts <- table(non_sign_feats$Filter, non_sign_feats$Type, non_sign_feats$Org, useNA = "ifany") %>% as.data.frame() %>% filter(Freq>0)
  
  colnames(signif_df_counts) <- c("Filter", "Type", "Org", "Freq")

  colnames(all_df_counts) <- c("Filter", "Type", "Org", "Total")

  counts_table <- merge(signif_df_counts, all_df_counts, all.x=F, all.y=T, by=c("Filter", "Type","Org"))
  
  counts_table <- counts_table %>% filter(Org=="forebrain anteroventral region")
  
  counts_table[is.na(counts_table)] <- 0
  
  counts_table <- counts_table %>% mutate(Prop=Freq/Total)
  
  counts_table$Type <- factor(counts_table$Type, levels = sort(unique(counts_table$Type)))
  
  # compute mean and standard error of the mean by subgroup
  summary_stat <- summarySE(counts_table,
  measurevar = "Prop",
  groupvars = c("Type", "Org")
  )
  summary_stat$Type <- factor(summary_stat$Type, levels = c("firstorder", "glcm", "gldm", "glrlm", "glszm", "ngtdm", "shape"))
  
  # plot mean and standard error of the mean
  ggplot(summary_stat, # remove NA level for Type
         aes(x = Type, y = Prop, fill=Type))+
    geom_col() +
    geom_errorbar(aes(ymin = Prop - se, ymax = Prop + se), # add error bars
    width = 0.1 # width of error bars
    ) +
    scale_y_continuous(limits=c(0,1))+
    labs(y = "Proportion of Features", x="Type")+
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1), 
          legend.position = "none")
}




plot_fully_pene_feats_as_percentages_just_av(significant_feats_sev, all_feats_sev)
plot_fully_pene_feats_as_percentages_just_av(significant_feats, all_feats)

```


```{r fig.width=4.5, fig.height=4}

quantify_rad_feats <- function(dataset, HPE_bros, signif_feats){
  
  #signif_feats <- signif_feats[(colnames(signif_feats) %in% c("vol",near_close))]
  
  significant_feats_means <- signif_feats %>% filter(vol %in% HPE_bros) %>% select_if(is.numeric) %>% colMeans()
  
  signif_feats <- signif_feats %>% dplyr::select(-vol)
  
  cluster_df <- create_cluster_df(signif_feats)
  
  #cluster_df$Type<-factor(cluster_df$Type, levels = c("firstorder","glcm","gldm","glrlm","glszm","ngtdm", "shape"))
  
  cluster_df$VolMean <- significant_feats_means
  
  pos_or_neg <- ifelse(significant_feats_means < 1, "Negative", "Positive")
  
  cluster_df$Correlation <- pos_or_neg
  
  split_by_corr <- split(cluster_df, cluster_df$Correlation)
  
  my_palette <- hcl.colors(7, palette = "Dark3")
  
  
  type_colors <- setNames(my_palette, c("firstorder","glcm","gldm","glrlm","glszm","ngtdm", "shape"))
  
  # Check if split_by_corr$Positive is empty
  is_positive_empty <- is.null(split_by_corr$Positive) || nrow(split_by_corr$Positive) == 0
  
  print(is_positive_empty)
  # Check if split_by_corr$Negative is NULL or empty
  is_negative_empty <- is.null(split_by_corr$Negative) || nrow(split_by_corr$Negative) == 0
  
  plot <- ggplot(mapping = aes(x = Type, y = log2(VolMean), col = Correlation)) +
    labs(x = "Feature Type", 
         y = expression("Log"[2] * "(" * frac("Mean HPE Embryo Measurement", "Mean Non-HPE Embryo Measurement") * ")"), 
       color = "Association of Feature")+
    theme_minimal()+
    scale_x_discrete(limits = c("firstorder","glcm","gldm","glrlm","glszm","ngtdm", "shape"))+
    scale_color_manual(values = c("Positive" = "red", "Negative" = "blue"))
  
  # Add Negative data if it's not empty
  if (!is_negative_empty) {plot <- plot +
      geom_boxplot(data = split_by_corr$Negative, width = 0.5, position = position_dodge(width = 0.75)) + 
      stat_summary(data = split_by_corr$Negative, fun.data = n_fun_neg, geom = "text", col = "blue", vjust = 2)
  }
  # Add Positive data if it's not empty
  if (!is_positive_empty) {plot <- plot +
    geom_boxplot(data = split_by_corr$Positive, width = 0.5, position = position_dodge(width = 0.75)) +
    stat_summary(data = split_by_corr$Positive, fun.data = n_fun_pos, geom = "text", col = "red", vjust = -1)
  }
  
  # panel wrap if needed 
  if (length(unique(cluster_df$Org))>4){plot <- plot +
    facet_wrap(~Org, scales = "fixed", nrow = 1, labeller = as_labeller(label_wrap_custom))+
    scale_y_continuous(limits = c(-3, 3), breaks = seq(-3, 3, by = 1))+
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1), 
          legend.position = c(0.975, 0.075), 
          legend.justification = c(0.975, 0.075),
          #legend.position = "right",
          legend.title = element_text(size = 10),
          strip.text = element_text(face = "bold", size = 10),
          legend.background = element_rect(color = alpha("black", 0.5), 
                                           fill = alpha("white", 0.5)))
    
  } else if (length(unique(cluster_df$Org))>1){plot <- plot +
    facet_wrap(~Org, scales = "fixed", nrow = 1)+
    scale_y_continuous(limits = c(-3, 3.35), breaks = seq(-3, 3, by = 1))+
     theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1), 
          legend.position = c(0.975, 0.075), 
          legend.justification = c(0.975, 0.075),
          #legend.position = "right",
          legend.title = element_text(size = 10),
          strip.text = element_text(face = "bold", size = 10),
          legend.background = element_rect(color = alpha("black", 0.5), 
                                           fill = alpha("white", 0.5)))}
  else{plot <- plot + 
    scale_y_continuous(limits = c(-2.25, 2.25), breaks = seq(-2, 2, by = 1))+
     theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1), 
          legend.position = c(0.975, 0.075), 
          legend.justification = c(0.975, 0.075),
          #legend.position = "right",
          legend.title = element_text(size = 10),
          strip.text = element_text(face = "bold", size = 10),
          legend.background = element_rect(color = alpha("black", 0.5), 
                                           fill = alpha("white", 0.5)))}
  
    
  
  print(plot)

}
  

label_wrap_custom <- function(variable) {
  sapply(variable, function(x) {
    if (nchar(x) > 12) {
      paste(strwrap(x, width = 12), collapse = "\n")
    } else {
      x
    }
  })
}



quantify_rad_feats(filt_dataset,  HPE_bros, significant_feats)


#quantify_rad_feats(filt_dataset_c3,  HPE_cohort_3_mild, significant_feats_c3)


quantify_rad_feats(filt_dataset_c3_phil,  HPE_cohort_3_phil, significant_feats_c3_phil)

quantify_rad_feats(filt_dataset_c3_ant,  HPE_cohort_3_ant, significant_feats_c3_ant)

# get plot of overlaps:

filt_dataset_over <- filt_dataset[,(intersect(colnames(filt_dataset_c3_ant), colnames(filt_dataset)))]

significant_feats_over <- significant_feats[colnames(significant_feats) %in% colnames(filt_dataset_over)]


#quantify_rad_feats(filt_dataset_over,  HPE_cohort_3_ant, significant_feats_c3_ant)
quantify_rad_feats(filt_dataset_over, HPE_bros, significant_feats_over)




```

```{r,  fig.width=9, fig.height=4.5}
quantify_rad_feats(filt_dataset_sev,  sev_HPE_bros, significant_feats_sev)

quantify_rad_feats(filt_dataset_c3_sev,  HPE_cohort_3_sev, significant_feats_c3_sev)

```

```{r, fig.width=6, fig.height=4}

prim_feats_in_second <- all_feats_c3[(all_feats_c3$vol %in% HPE_cohort_3_ant),(colnames(all_feats_c3) %in% colnames(filt_dataset))]

prim_feats_in_second

percentage_not_equal_1 <- function(column) {
  not_equal_1 <- sum(column != 1)
  total <- length(column)
  percentage <- (not_equal_1 / total) * 100
  return(percentage)
}

percentages_in_second <- sapply(prim_feats_in_second, percentage_not_equal_1)


data.frame(percentages_in_second)

perc_data <- data.frame(percentages_in_second) %>% filter(percentages_in_second == 87.5)

quantify_rad_feats(filt_dataset_over, HPE_bros, significant_feats_over)


near_close <- rownames(perc_data)


filt_dataset_87 <- filt_dataset[,(c("vol",near_close))]

significant_feats_87 <- significant_feats[colnames(significant_feats) %in% c("vol",near_close)]

quantify_rad_feats(filt_dataset_87, HPE_bros, significant_feats_87)


near_close
```

```{r setup}

library(ComplexHeatmap)
library(circlize)
# Find non-volumetric shape differences
get_non_vol_diffs <- function(fully_pene_feats, searchstr) {
  diffs_tab <- create_cluster_df(fully_pene_feats) %>% split(.$Org)
  all_df_tab <- create_cluster_df(fully_pene_feats) %>% split(.$Org)
  
  vol_diffs <- sapply(all_df_tab, function(x) any(str_detect(x$Stat, "VoxelVolume")))
  groups_to_remove <- sapply(all_df_tab, function(x) any(str_detect(x$Type, "shape")))
  negative_spaces <- sapply(all_df_tab, function(x) any(str_detect(x$Org, "ventricle|cavity|vesicle")))
  
  shape_diffs <- tryCatch({
  do.call(rbind, diffs_tab[groups_to_remove & !vol_diffs]) %>% filter(Type == "shape")
}, error = function(e) {
  message("Error in rbind or filter: Returning an empty tibble.")
  tibble()
})
  
  print(shape_diffs)

  text_diffs <- do.call(rbind, diffs_tab[!(groups_to_remove | negative_spaces)])
  
  all_diffs <- do.call(rbind, all_df_tab) %>% filter(!((Type != "shape") & str_detect(Org, "ventricle|cavity|vesicle")))

  print(all_diffs)
  
  list(
    df = text_diffs, cols = if (length(text_diffs) > 0) combine_rows_to_vector(text_diffs) else character(),
    shape_df = shape_diffs, shape_cols = if (length(shape_diffs) > 0) combine_rows_to_vector(shape_diffs) else character(),
    all_df = all_diffs, all_cols = if (length(all_diffs) > 0) combine_rows_to_vector(all_diffs) else character()
  )
}

# Performs hierarchairal clustering using increasing k and gets the best silhoutte score
# clusters the with optimal k. 
auto_cluster <- function(df, cor_matrix) {
  
  # Compute the distance matrix from the correlation matrix, use dissimiliarity instead of similarity
  dist_matrix <- as.dist(1 - abs(cor_matrix))
  #dist_matrix <- dist(cor_matrix)
  
  # dbscan of corr_matrix for feature outlier removal
  dbscan_result <- dbscan(dist_matrix, eps = 0.3, minPts = 5)
  
  
  # The features classified as noise (0) are outliers
  outliers_dbscan <- which(dbscan_result$cluster == 0)
  
  print(outliers_dbscan)
  #keep_features <- setdiff(1:ncol(cor_matrix), outliers_dbscan)
  
  
  #cor_matrix <- cor_matrix[keep_features, keep_features]
  
  #dist_matrix <- as.dist(1 - abs(cor_matrix))
  
  # Perform hierarchical clustering
  hclust_res <- hclust(dist_matrix)

  # Convert to dendrogram
  #dend <- as.dendrogram(hclust_res)
  
  #dend %>% plot
  
  k_num <- ifelse(ncol(df) < 50, ncol(df)-1, 50)
    
  sil_scores <- numeric(k_num)  # Try k = 2 to 10
  for (k in 2:k_num) {
    cluster_labels <- cutree(hclust_res, k_num)
    sil_scores[k] <- mean(silhouette(cluster_labels, dist_matrix)[, 3])
    }
  # Find the best number of clusters
  print(plot(1:k_num, sil_scores, type = "b", xlab = "Number of clusters", ylab = "Silhouette Score"))
  
  optimal_k <- which.max(sil_scores)
  
  
  optimal_clusters <- cutree(hclust_res, k = optimal_k)

  
  return(list(dbs_clus=dbscan_result$cluster, sil_clus = optimal_clusters))
    
  }
  
#kdhkfdskads

plot_differences <- function(rad_df, cols){
  
  filtered_dataset <- rad_df[colnames(rad_df) %in% c(cols, "Genotype", "Background","HPE", "WEV", "vol")]
  
  #filtered_dataset <- arrange(transform(filtered_dataset, Background=ordered(Background,levels=c("C3H","C57BL6"))))
  
  #filtered_dataset <- arrange(transform(filtered_dataset, Genotype=ordered(Genotype,levels=c("WT","HET"))))
  
  rad_plots <- lapply(seq_along(filtered_dataset[,2:(length(names(filtered_dataset))-3)]), function(data) {
  ggplot(filtered_dataset,aes(x=WEV,y=filtered_dataset[,2:(length(names(filtered_dataset))-3)][[data]],colour=interaction(Background, Genotype)))+
    #geom_boxplot()+
    geom_point()+
    geom_smooth(method = "lm", level=0.999)+
    #facet_grid(Background, scales = "free_x")+
    facet_grid(~Background, labeller = back_labeller, scales = "free_x")+
    
    scale_color_manual(name="", labels=unlist(inter_names_v2), values=c("#F8766D","#FFA500","#00BFC4",'#C77CFF'))+
                                                                                   #scale_x_discrete(labels=unlist(variable_names))+
    
    #scale_color_manual(name="", labels=c("non-HPE", "overt-HPE"), values=c("#F8766D","#00BFC4"))+
    #                                                                               #scale_x_discrete(labels=unlist(variable_names))+
    
    ylab(expression("Radiomics Measurement Normalised to WEV"))+
    ggtitle(names(filtered_dataset[,2:(length(names(filtered_dataset))-3)][[data]]))+
    xlab(expression("Whole Embryo Volume (WEV) mm"^3))+
    ggtitle(gsub("_", " ", names(filtered_dataset[,2:(length(names(filtered_dataset))-3)])[data]))+
    theme(plot.subtitle=element_text(size=10, hjust=0.5),
          strip.text.x = element_text(hjust = 0.5, size = 10), legend.position = "none",
          title = element_text(size=10, hjust=0.5),
          axis.title.x = element_text(size=12), 
          axis.title.y = element_text(size=12))
    #labs(tag = "B")
})
  
  print(rad_plots)
  
}







```



```{r, fig.height=9, fig.width=11, warning=T, message=FALSE}
#  fig.height=9, fig.width=11
#3.5, 5.5
#fig.height=14, fig.width=14
#9, fig.width=10


determine_feat_imp <- function(df, cols, test_effect, corr_removal=F){
  
  if (corr_removal){
    
    df_for_corr <- df %>% dplyr::select(is.numeric) %>% select(-WEV)
    
    cor_matrix <- cor(df_for_corr, method = "spearman")
    
    high_corr <- findCorrelation(cor_matrix, cutoff = 0.9)
    
    filtered_df <- df_for_corr[, -high_corr, drop=F]
    
    df <- df[colnames(df) %in% c(colnames(filtered_df), "Genotype", "Background", "HPE","WEV", "vol")]
    
  }
  
  library(reshape2)
  library(catboost)
  
  fit_params <- list(iterations = 1000,
                   loss_function = 'Logloss',
                   task_type = 'CPU', verbose=100)
  
  
  bin_levels <- levels(df[[test_effect]])
  
  df[[test_effect]] <- ifelse(df[[test_effect]] == bin_levels[1], 0, 1)
  
  df_train <- df[, sapply(df, is.numeric)] %>% dplyr::select(-all_of(test_effect)) %>% select(-WEV)
  
  # Create the test pool using the dynamically selected column
  test_pool <- catboost::catboost.load_pool(df_train, label = df[[test_effect]])
    
  
  
  cat_model <- catboost.train(test_pool, params=fit_params)
  
  shp <- shapviz(cat_model, X_pred = test_pool, X = df_train)
 
  p <- sv_importance(shp, kind="beeswarm")+
    scale_color_gradient(
    low = "blue", high = "red",
    guide = guide_colorbar(
      title.position = "left",  # Move title to the left of the legend
      title.hjust = 0.5,  # Center the vertical title
      barwidth = 0.5,  # Adjust width of color bar
      barheight = 8  # Adjust height of color bar for better visibility
    ),  # Ensure the color bar has ticks
    labels = function(x) ifelse(x == 0, "Low", ifelse(x == 1, "High", ""))  # Rename labels
  ) + theme(legend.title = element_text(angle = 90))
  print(p)
  
  shap_values <- get_shap_values(shp)
  shap_importance <- colMeans(abs(shap_values))  # Mean absolute SHAP per feature
  
  # Rank features by SHAP importance
  feature_rank <- data.frame(Feature = colnames(df_train), Importance = shap_importance)
  feature_rank <- feature_rank[order(-feature_rank$Importance), ]  # Sort descending
  
  # Define the feature count grid (1 to 29 features)
  feature_counts <- seq(1, min(29, ncol(df_train)))  # Ensure max is within range
  results <- data.frame(N_Features = integer(), Mean_Accuracy = numeric())
  
  # Train models with increasing numbers of features
  for (n in feature_counts) {
    print(paste("doing n: ",n ))
    selected_features <- head(feature_rank$Feature, n)
    x_selected <- df_train[, selected_features, drop = FALSE]  # Keep as dataframe
    
    # Cross-validation setup
    fit_control <- trainControl(method = "LOOCV", number = 10, verboseIter = 500, classProbs = TRUE)  # 10-fold CV
    # Train model using only selected features
    model_cv <- train(x_selected, as.factor(make.names((df[[test_effect]]))), method = catboost.caret,
                      tuneGrid = data.frame(depth = 6, learning_rate = 0.1, iterations = 1000,
                                            l2_leaf_reg = 1e-3, rsm = 0.95, border_count = 64),
                      trControl = fit_control, verbose=500)
    
    # Store mean accuracy across CV folds
    mean_acc <- mean(model_cv$results$Accuracy)
    results <- rbind(results, data.frame(N_Features = n, Mean_Accuracy = mean_acc))
    }
  
  # Find best feature count
  best_n <- results$N_Features[which.max(results$Mean_Accuracy)]
  best_features <- head(feature_rank$Feature, best_n)
  
  # Train final model with best N features
  x_best <- df_train[, best_features, drop = FALSE]
  
  final_test_pool <- catboost::catboost.load_pool(x_best, label = df[[test_effect]])
  
  final_model <- catboost.train(final_test_pool, params=fit_params)
  
  # Print best feature count and selected features
  print(paste("Optimal number of features:", best_n))
  
  # Plot feature count vs mean accuracy
  p<-ggplot(results, aes(x = N_Features, y = Mean_Accuracy)) +
    geom_line() + geom_point() +
    labs(title = "Feature Count vs Mean Accuracy", x = "Number of Features", y = "Mean Accuracy")
  print(p)
  shp <- shapviz(final_model, X_pred = final_test_pool, X = df_train)
 
  p <- sv_importance(shp, kind="beeswarm")+
    scale_color_gradient(
    low = "blue", high = "red",
    guide = guide_colorbar(
      title.position = "left",  # Move title to the left of the legend
      title.hjust = 0.5,  # Center the vertical title
      barwidth = 0.5,  # Adjust width of color bar
      barheight = 8  # Adjust height of color bar for better visibility
    ),  # Ensure the color bar has ticks
    labels = function(x) ifelse(x == 0, "Low", ifelse(x == 1, "High", ""))  # Rename labels
  ) + theme(legend.title = element_text(angle = 90))
  print(p)
}

plot_cor <- function(df, cor_matrix, clusters, correlated_vol_feats, correlated_shape_feats, shape_plot, cor_checked, corr_networks=F){
  
  #dist_matrix <- dist(cor_matrix)
  dist_matrix <- as.dist(1 - abs(cor_matrix))
  
  # Apply agglomerative hierarchical clustering on the new distance matrix
  hc <- hclust(dist_matrix)
  
  #method = "ward.D2"
  
  #breaks <- seq(-1, 1, length.out = 100)
  breaks <- seq(0, 1, length.out = 100)
  
  colors <- colorRampPalette(brewer.pal(9, "YlOrRd"))(length(breaks))
  
  #colors <- colorRampPalette(rev(brewer.pal(11, "RdYlBu")))(length(breaks))
  
  small_mat<- ifelse(ncol(cor_matrix)<70, T, F)
  
  xsmall_mat <- ifelse(ncol(cor_matrix)<30, T, F)
  
  vol_corr_as_anno <- ifelse(rownames(cor_matrix) %in% correlated_vol_feats, "Yes", "No")
  
  
  ann_colors <- list()
  
  dbscan_levels <- levels(factor(clusters$dbs_clus))
  
  hca_levels <- levels(factor(clusters$sil_clus))
  
  all_required_colors <- length(dbscan_levels) + length(hca_levels)-1
  
  extended_palette <- if (all_required_colors > 9) colorRampPalette(brewer.pal(9, "Set1"))(all_required_colors) else brewer.pal(9, "Set1")
  
  dbscan_colors <- "grey"
  
  dbscan_palette <- c(dbscan_colors, extended_palette[1:(length(dbscan_levels)-1)])

  ann_colors$DBSCAN <- setNames(dbscan_palette, dbscan_levels)
  
    
  # Use RColorBrewer's Set1 palette for DBSCAN
  ann_colors$DBSCAN <- setNames(brewer.pal(length(dbscan_levels), "Set1"), dbscan_levels)
  
  ann_colors$DBSCAN <- ann_colors$DBSCAN[!is.na(names(ann_colors$DBSCAN))]
  
  hca_palette <- extended_palette[length(dbscan_levels):all_required_colors]
  
    
  # Use the same palette for HCA Cutree
  ann_colors$HCA.Cutree <- setNames(hca_palette, hca_levels)
  ann_colors$HCA.Cutree <- ann_colors$HCA.Cutree[!is.na(names(ann_colors$HCA.Cutree))]
  
  

  if (corr_networks){
  
    
    corr_network_levels <- levels(factor(clusters$corr_networks))
  
    
    all_required_colors <- all_required_colors + length(corr_network_levels)-1
    
    print(length(corr_network_levels))
    
    print(all_required_colors)
    
    
    extended_palette <- if (all_required_colors > 9) colorRampPalette(brewer.pal(9, "Set1"))(all_required_colors) else brewer.pal(9, "Set1")
    print(extended_palette)
    
    # reset the palettes
    dbscan_colors <- "grey"
    
    dbscan_palette <- c(dbscan_colors, extended_palette[1:(length(dbscan_levels)-1)])
    
    print(dbscan_palette)
    ann_colors$DBSCAN <- setNames(dbscan_palette, dbscan_levels)
    
    ann_colors$DBSCAN <- ann_colors$DBSCAN[!is.na(names(ann_colors$DBSCAN))]
    
    print((all_required_colors - (length(corr_network_levels) - 1)))
    
    print((length(dbscan_levels)):(length(dbscan_levels)+length(hca_levels)-1))
    
    hca_palette <- extended_palette[(length(dbscan_levels)):(length(dbscan_levels)+length(hca_levels)-1)]
    
    print(hca_palette)

    
    # Use the same palette for HCA Cutree
    
    ann_colors$HCA.Cutree <- setNames(hca_palette, hca_levels)
    ann_colors$HCA.Cutree <- ann_colors$HCA.Cutree[!is.na(names(ann_colors$HCA.Cutree))]
    
    cor_colors <- "grey"
    print((length(dbscan_levels)+length(hca_levels)-1))
    
    print((length(dbscan_levels)+length(hca_levels)):all_required_colors)
    
    corr_network_palette <- c(cor_colors, extended_palette[(length(dbscan_levels)+length(hca_levels)):all_required_colors])
    
    
    print(corr_network_palette)
    ann_colors$Corr.Network <- setNames(corr_network_palette, corr_network_levels)
    ann_colors$Corr.Network <- ann_colors$Corr.Network[!is.na(names(ann_colors$Corr.Network))]
    
    rownames(cor_matrix) <- str_replace_all(rownames(cor_matrix), "_", " ")
    colnames(cor_matrix) <- str_replace_all(colnames(cor_matrix), "_", " ")
    row_annotation <- data.frame(
      DBSCAN = factor(clusters$dbs_clus),
      HCA.Cutree = factor(clusters$sil_clus),
      Corr.Network = factor(clusters$corr_networks))
    
    
    
    
  }
  
   else if (cor_checked){
     rownames(cor_matrix) <- str_replace_all(rownames(cor_matrix), "_", " ")
     colnames(cor_matrix) <- str_replace_all(colnames(cor_matrix), "_", " ")
    
    
    row_annotation <- data.frame(
      DBSCAN = factor(clusters$dbs_clus),
      HCA.Cutree = factor(clusters$sil_clus))
    
  } else if (!shape_plot){
    
    shape_corr_as_anno <- ifelse(rownames(cor_matrix) %in% correlated_shape_feats, "Yes", "No")
    
    rownames(cor_matrix) <- str_replace_all(rownames(cor_matrix), "_", " ")
    colnames(cor_matrix) <- str_replace_all(colnames(cor_matrix), "_", " ")
    
    ann_colors$Correlated.With.Volume = c("Yes" = "cyan", "No" = "gray")
    
    vol_corr_as_anno <- ifelse(rownames(cor_matrix) %in% correlated_vol_feats, "Yes", "No")
    
    
    row_annotation <- data.frame(
      Correlated.With.Volume = vol_corr_as_anno,
      Correlated.With.Shape = shape_corr_as_anno,
      DBSCAN = factor(clusters$dbs_clus),
      HCA.Cutree = factor(clusters$sil_clus))
    
    ann_colors$Correlated.With.Shape <- c("Yes" = "blue", "No" = "gray")
    ann_colors$Correlated.With.Volume = c("Yes" = "cyan", "No" = "gray")
    # Generate consistent colors using palettes for DBSCAN and HCA Cutree
    
  } else {
    
    # simplify names for shape features
    rownames(cor_matrix) <- str_replace_all(rownames(cor_matrix), "original", "")
    colnames(cor_matrix) <- str_replace_all(colnames(cor_matrix), "original", "")
    rownames(cor_matrix) <- str_replace_all(rownames(cor_matrix), "shape", "")
    colnames(cor_matrix) <- str_replace_all(colnames(cor_matrix), "shape", "")
    rownames(cor_matrix) <- str_replace_all(rownames(cor_matrix), "_", " ")
    colnames(cor_matrix) <- str_replace_all(colnames(cor_matrix), "_", " ")
    rownames(cor_matrix) <- str_replace_all(rownames(cor_matrix), "  ", "")
    colnames(cor_matrix) <- str_replace_all(colnames(cor_matrix), "  ", "")
    
    
    ann_colors$Correlated.With.Volume = c("Yes" = "cyan", "No" = "gray")
    
    vol_corr_as_anno <- ifelse(rownames(cor_matrix) %in% correlated_vol_feats, "Yes", "No")
    
    
    row_annotation <- data.frame(
    Correlated.With.Volume = vol_corr_as_anno,
    DBSCAN = factor(clusters$dbs_clus),
    HCA.Cutree = factor(clusters$sil_clus))
    
  }
  
  rownames(row_annotation) <- rownames(cor_matrix)
  
  col_fun <- colorRamp2(breaks, colors)
  
  # Create row annotation object
  ha <- rowAnnotation(
    df = row_annotation,
    col = ann_colors)
  
  cell_fun = function(j, i, x, y, width, height, fill) {
    grid.text(round(1 - abs(cor_matrix[i, j]), 2), x, y, gp = gpar(fontsize = 8, col = "black"))
  }
  
  #cellwidth = 20, cellheight = 20, display_numbers = T, 
  if (small_mat){
    # p <- pheatmap(cor_matrix, clustering_distance_rows = "euclidean", clustering_distance_cols = "euclidean",
    #             legend = T, annotation_colors = ann_colors,
    #              show_rownames = T, show_colnames = F,
    #              annotation_row =row_annotation, colors=colors, breaks = breaks)
    # 
    p <- Heatmap(
  (1 - abs(cor_matrix)),
  name = paste0("Dissimilarity (1 - |", "\u03C1", "|)"),
  col = col_fun,
  cell_fun = if (xsmall_mat) {
    function(j, i, x, y, width, height, fill) {
      grid.text(round(1 - abs(cor_matrix[i, j]), 2), x, y, gp = gpar(fontsize = 8, col = "black"))
    }
  } else {
    NULL
  },
  #clustering_distance_rows = "euclidean",
  #clustering_distance_columns = "euclidean",
  cluster_rows = hc,
  cluster_columns = hc,  # Custom column clusterin
  show_row_names = TRUE,
  show_column_names = FALSE,
  row_names_side = "right",
  column_names_side = NULL,
  row_names_gp = gpar(fontsize = 10),
  left_annotation = ha,
  heatmap_legend_param = list(direction = "horizontal") # Ensures horizontal legend
)
  } else {
    # p <- pheatmap(cor_matrix, clustering_distance_rows = "euclidean", clustering_distance_cols = "euclidean",
    #               show_rownames = F, show_colnames = F, annotation_colors = ann_colors,
    #              annotation_row =row_annotation, colors=colors, breaks = breaks, legend = T)
     p <- Heatmap(
  (1 - abs(cor_matrix)),
  name = paste0("Dissimilarity (1 - |", "\u03C1", "|)"),
  col = col_fun,
  #clustering_distance_rows = "euclidean",
  #clustering_distance_columns = "euclidean",
  cluster_rows = hc,
  cluster_columns = hc,
  show_row_names = FALSE,
  show_column_names = FALSE,
  row_names_side = NULL,
  column_names_side = NULL,
  left_annotation = ha,
  heatmap_legend_param = list(direction = "horizontal") # Ensures horizontal legend
)
  }
  
  #grid.text("Spearman's Coefficient", x = 0.9, y = 0.85, gp = gpar(fontsize = 12, fontface = "bold"))
  
  
  draw(p, heatmap_legend_side = "bottom", padding = unit(c(4, 0.5, 0.5, 7), "cm"))
}


determine_cor_to_ex <- function(searchstr, df, drop_searchstr){
  #stupid default r function stuff
  if(missing(drop_searchstr)){drop_searchstr=T}
  
  cor_matrix <- cor(df, method = "spearman")
  
  features <- grep(searchstr, colnames(df), ignore.case = TRUE, value = TRUE)
  cor_with <- which(colnames(df) %in% features)
  correlated_with_ind <- which(apply(abs(cor_matrix[, cor_with, drop = FALSE]), 1, max) >= 0.9)
  correlated_features <- colnames(df)[correlated_with_ind]
  if (drop_searchstr) {correlated_features <-correlated_features[!grepl(searchstr, correlated_features)]}
  return(correlated_features)
    }


check_cor <- function(df, cols, shape_plot){
  
  df <- df[colnames(df) %in% c(cols, "Genotype", "Background", "HPE","WEV", "vol")]
  
  df_orig <-df
  
  library(caret)
  
  
  df <- df %>% dplyr::select(where(is.numeric)) %>% dplyr::select(-WEV)

  
  cor_matrix <- cor(df, method = "spearman")

  
  correlated_vol_feats <- determine_cor_to_ex("Volume_", df)
  
  print("correlated vol feats")
  print(correlated_vol_feats)
  
  
  correlated_shape_feats <- determine_cor_to_ex("shape", df)
  
  print("correlated shape feats")
  print(correlated_shape_feats)
  
  
  if (ncol(df) < 3) {
     df <- df[, !colnames(df) %in% c(correlated_vol_feats, correlated_shape_feats), drop = FALSE]
    final_df <- df_orig[colnames(df_orig) %in% c(colnames(df))]
    
    return(final_df)
    
  }
  
  
  optimal_clusters_bef <- auto_cluster(df, cor_matrix)
  
  #plot_cor(df, cor_matrix, optimal_clusters_bef, correlated_vol_feats, correlated_shape_feats, shape_plot, cor_checked=F) 
  
  df <- df[, !colnames(df) %in% c(correlated_vol_feats, correlated_shape_feats), drop = FALSE]

  cor_matrix <- cor_matrix[!colnames(cor_matrix) %in% c(correlated_vol_feats, correlated_shape_feats), 
                         !colnames(cor_matrix) %in% c(correlated_vol_feats, correlated_shape_feats), 
                         drop = FALSE]
  
  optimal_clusters_bef <- auto_cluster(df, cor_matrix)
  
  #plot_cor(df, cor_matrix, optimal_clusters_bef, correlated_vol_feats, correlated_shape_feats, shape_plot, cor_checked=T) 
  
  #drop corr
  
  
  high_corr <- findCorrelation(cor_matrix, cutoff = 0.9)
  
  print("high corr")
  
  print(colnames(df[, high_corr]))
  
  filtered_df <- df[, -high_corr, drop=F]
  
  if (ncol(filtered_df) < 3){
  
    final_df <- df_orig[colnames(df_orig) %in% c(colnames(filtered_df))]
    
    return(final_df)
  }
  
  cor_matrix<-cor(filtered_df, method = "spearman", use = "pairwise.complete.obs")

  optimal_clusters_aft <- auto_cluster(filtered_df, cor_matrix)
  
  #plot_cor(filtered_df, cor_matrix, optimal_clusters_aft, correlated_vol_feats, correlated_shape_feats, shape_plot, cor_checked=T)
  
  #corr_matrix after removing potential correlated features
  
  
  
  final_df <- df_orig[colnames(df_orig) %in% c(colnames(filtered_df))]
  
  return(final_df)
  }


determine_cor_groups <- function(searchstr, df, drop_searchstr = TRUE, cor_threshold = 0.9) {
  library(ggraph)
  library(ggrepel)
  library(widyr)
  cor_matrix <- cor(df, method = "spearman")
  
  # Identify features matching the search string
  features <- grep(searchstr, colnames(df), ignore.case = TRUE, value = TRUE)
  cor_with <- which(colnames(df) %in% features)
  
  # Identify highly correlated features
  correlated_with_ind <- which(apply(abs(cor_matrix[, cor_with, drop = FALSE]), 1, max) >= cor_threshold)
  correlated_features <- colnames(df)[correlated_with_ind]
  
  if (drop_searchstr) {
    correlated_features <- correlated_features[!grepl(searchstr, correlated_features)]
  }
  
  if (length(correlated_features) == 0) {
    return(data.frame(Feature = character(0), Group = integer(0)))
  }
  
  # Extract relevant part of the correlation matrix
  sub_cor_matrix <- cor_matrix[correlated_features, correlated_features]
  
  sub_cor_matrix <- cor_matrix
  
  # Find feature pairs that meet the threshold
  cor_pairs <- which(abs(sub_cor_matrix) >= cor_threshold, arr.ind = TRUE)
  #cor_pairs <- which(upper.tri(cor_matrix), arr.ind = TRUE)
  
  # Create dataframe of feature pairs
  cor_df <- data.frame(
    Feature1 = rownames(sub_cor_matrix)[cor_pairs[, 1]],
    Feature2 = colnames(sub_cor_matrix)[cor_pairs[, 2]]
  ) |> unique()
  
  cor_df$weight <- sub_cor_matrix[cor_pairs]
  
  # Remove self-correlations
  cor_df <- cor_df[cor_df$Feature1 != cor_df$Feature2, ]
  
  
  if (nrow(cor_df) == 0) {
    return(data.frame(Feature = correlated_features, Group = seq_along(correlated_features))) 
  }
  

  
  #test corr network from: https://www.tidytextmining.com/nasa.html?q=correlation%20ne#networks-of-keywords
  cor_long <- as.data.frame(as.table(sub_cor_matrix)) %>%
  dplyr::rename(Feature1 = Var1, Feature2 = Var2, correlation = Freq) %>%
  dplyr::filter(Feature1 != Feature2) %>% # Remove self-correlations
  filter(abs(correlation) > 0.9)
  
  g <- graph_from_data_frame(cor_long, directed=F)
  
  components <- components(g)
  
  
  group_map <- setNames(components$membership, names(components$membership))
  
  # Match the row names of cor_mat with df and assign group values
  group_assignment <- ifelse(rownames(cor_matrix) %in% names(components$membership), group_map[rownames(cor_matrix)], 0)
  
  # Convert to a named vector
  names(group_assignment) <- rownames(cor_matrix)
  
  
  
  cor_long$Feature1 <- str_replace_all(cor_long$Feature1, "original", "")
  cor_long$Feature1 <- str_replace_all(cor_long$Feature1, "shape", "")
  cor_long$Feature1 <- str_replace_all(cor_long$Feature1, "__", "")
  
  cor_long$Feature2 <- str_replace_all(cor_long$Feature2, "original", "")
  cor_long$Feature2 <- str_replace_all(cor_long$Feature2, "shape", "")
  cor_long$Feature2 <- str_replace_all(cor_long$Feature2, "__", "")
  
  
  g <- graph_from_data_frame(cor_long, directed=F) 
  
  E(g)$correlation <- cor_long$correlation
  p<-ggraph(g, layout = "fr") +
   geom_edge_link(aes(
    edge_alpha = abs(E(g)$correlation),  # Use correlation from edge attributes
    #edge_width = abs(E(g)$correlation),  # Use correlation from edge attributes
    edge_colour = E(g)$correlation),  # Use correlation for edge color
    show.legend = TRUE) +
  geom_node_point(size = 4, alpha = 0.7) +
  geom_node_text(aes(label = name), repel = TRUE,
                 box.padding = unit(3, "lines"))+
  theme_void()+
    scale_edge_colour_gradient2(
    low = "blue",  # Negative correlation (blue)
    mid = "grey",  # Mid-point (neutral correlation)
    high = "red",  # Positive correlation (red)
    midpoint = 0   # Midpoint is 0 for neutral correlations
  )
  
  print(p)
  
  
  
  
  return(group_assignment)
}


get_and_plots_differences <- function(rad_df, fully_pene_feats, test_effect) {
  
  colnames(rad_df) <- str_remove(colnames(rad_df), "wavelet_")
  
  diffs <- get_non_vol_diffs(fully_pene_feats, searchstr)
  
  # Shape analysis
  # if (length(diffs$shape_cols) > 0) {
  #   if (length(diffs$shape_cols) <= 20) {
  #     print("HANDFUL OF SHAPE COLS FOUND")
  #     plot_differences(rad_df, diffs$shape_cols)
  #   }
  #   
  #   print(diffs$shape_df)
  #   shape_reduced_df <- check_cor(rad_df, diffs$shape_cols, shape_plot=T)
  #   
  #   if (ncol(shape_reduced_df) > 0) {
  #     if (ncol(shape_reduced_df) <= 20) {
  #       print("HANDFUL OF NON-CORR SHAPE COLS FOUND")
  #     }
  #     
  #     plot_differences(shape_reduced_df, diffs$shape_cols)
  #     do_PCA(shape_reduced_df)
  #     determine_feat_imp(shape_reduced_df, diffs$shape_cols, test_effect)
  #   }
  # }
  # 
  # # Text analysis
  # if (length(diffs$cols) > 0) {
  #   if (length(diffs$cols) <= 20) {
  #     print("HANDFUL OF TEXT COLS FOUND")
  #     plot_differences(rad_df, diffs$cols)
  #   }
  #   
  #   text_reduced_df <- check_cor(rad_df, diffs$cols, shape_plot=F)
  #   
  #   if (ncol(text_reduced_df) > 0) {
  #     if (ncol(text_reduced_df) <= 20) {
  #       print("HANDFUL OF NON-CORR TEXT COLS FOUND")
  #     }
  #     #plot_differences(text_reduced_df, diffs$cols)
  #     do_PCA(text_reduced_df)
  #     determine_feat_imp(text_reduced_df, diffs$cols, test_effect)
  #   }
  # }
  
  # All differences analysis
  if (length(diffs$all_cols) > 0) {
    #str(diffs$all_cols)
    
    diffs_by_org <- diffs$all_df %>% split(.$Org)
  
    cols_by_org <- lapply(diffs_by_org, function(org_diffs) {combine_rows_to_vector(org_diffs)})
  
    corr_rem_by_org <- lapply(cols_by_org, function(org_cols){check_cor(rad_df, org_cols, shape_plot=F)}) 
    
    
    all_reduced_df <- bind_cols(corr_rem_by_org)
    
    all_reduced_df <- rad_df[colnames(rad_df) %in% c(colnames(all_reduced_df), "Genotype", "Background", "HPE", "WEV", "vol")]
    
    df_for_corr <- all_reduced_df%>% dplyr::select(where(is.numeric)) %>% dplyr::select(-WEV)
    
    cor_matrix <- cor(df_for_corr, method = "spearman")
    
    optimal_clusters <- auto_cluster(df_for_corr, cor_matrix)
    
    
    correlated_vol_feats <- determine_cor_groups("Volume_", df_for_corr, drop_searchstr = F)
    
  
    print("correlated vol feats - inter-organ")
    
    print(correlated_vol_feats)
    print(optimal_clusters$dbs_clus)
    
    
    correlated_shape_feats <- determine_cor_groups("shape", df_for_corr, drop_searchstr = F)
    
    print("correlated shape feats - inter-organ")
    print(correlated_shape_feats)
    
    print(optimal_clusters)
    optimal_clusters$corr_networks <- correlated_vol_feats
    
    
    plot_cor(all_reduced_df, cor_matrix, optimal_clusters, correlated_vol_feats, correlated_shape_feats, shape_plot=F, cor_checked=T, corr_networks=T)
    
    #reduced_df_for_ml <- check_cor(all_reduced_df, colnames(all_reduced_df))
    
    
    if (ncol(all_reduced_df) > 0) {
      do_PCA(all_reduced_df)
      
      if (ncol(all_reduced_df) < 50) {plot_differences(all_reduced_df, diffs$all_cols)}
      
      write.csv(all_reduced_df, paste(test_effect, "_all_output.csv"))
      determine_feat_imp(all_reduced_df, diffs$all_cols, test_effect, corr_removal = T)
    }
  }
}



do_PCA <- function(df){
  df <- df %>% dplyr::select(where(is.numeric))
  
  
  pca_result <- prcomp(df, center = TRUE, scale. = TRUE)
  loadings_pc1 <- abs(pca_result$rotation[, 1])  # Take absolute values
  top_features <- sort(loadings_pc1, decreasing = TRUE)  # Sort by contribution
print(barplot(sort(abs(pca_result$rotation[,1]), decreasing = TRUE), las = 2, main = "PC1 Loadings"))

df_rot <-t(df)

dbscan_result <- dbscan(df_rot,  eps = 0.3, minPts = 5)

print(dbscan_result)


p<- fviz_cluster(dbscan_result, df_rot, geom = "point", pointsize = 2)
print(p)

}


get_and_plots_differences(rad_info, geno_fully_pene_feats, "Genotype")





```


```{r, fig.height=15, fig.width=15}

get_and_plots_differences(rad_info, back_fully_pene_feats, "Background")

```


```{r, fig.height=7, fig.width=11}

HPE_sign <- rad_info[colnames(rad_info) %in% c(colnames(significant_feats), "Genotype", "Background", "WEV", "vol")]


HPE_sign$HPE <- factor(ifelse(HPE_sign$vol %in% HPE_bros, 1, 0))

HPE_significant_feats <- significant_feats %>% select(-vol)



get_and_plots_differences(HPE_sign, HPE_significant_feats, "HPE")

```


```{r}
#int_shape_diffs_v2 <- get_non_vol_shape_diffs(int_fully_pene_feats_v2)
#int_shape_diffs_v2


# plot features

label_wrap_custom <- function(variable) {
  sapply(variable, function(x) {
    if (nchar(x) > 25) {
      paste(strwrap(x, width = 25), collapse = "\n")
    } else {
      x
    }
  })
}



plot_volumes_only <-  function(rad_df){
  
  vol_cols <- colnames(rad_df)[grep("VoxelVolume", colnames(rad_df))]
  
  filtered_dataset <- rad_df[colnames(rad_df) %in% c(vol_cols, "Genotype", "Background", "WEV", "vol")]
  
  #filtered_dataset <- arrange(transform(filtered_dataset, Background=ordered(Background,levels=c("C3H","C57BL6"))))
  
  #filtered_dataset <- arrange(transform(filtered_dataset, Genotype=ordered(Genotype,levels=c("WT","HET"))))
  
  rad_plots <- lapply(seq_along(filtered_dataset[,2:(length(names(filtered_dataset))-3)]), function(data) {
  ggplot(filtered_dataset,aes(x=WEV,y=filtered_dataset[,2:(length(names(filtered_dataset))-3)][[data]],colour=interaction(Background, Genotype)))+
    #geom_boxplot()+
    geom_point()+
    geom_smooth(method = "lm", level=0.999)+
    #facet_grid(Background, scales = "free_x")+
    facet_grid(~Background, labeller = back_labeller, scales = "free_x")+
    
    scale_color_manual(name="", labels=unlist(inter_names_v2), values=c("#F8766D","#FFA500","#00BFC4",'#C77CFF'))+
                                                                                   #scale_x_discrete(labels=unlist(variable_names))+
    
    #scale_color_manual(name="", labels=c("non-HPE", "overt-HPE"), values=c("#F8766D","#00BFC4"))+
    #                                                                               #scale_x_discrete(labels=unlist(variable_names))+
    
    ylab(expression("Radiomics Measurement Normalised to WEV"))+
    ggtitle(names(filtered_dataset[,2:(length(names(filtered_dataset))-3)][[data]]))+
    xlab(expression("Whole Embryo Volume (WEV) mm"^3))+
    guides(color = guide_legend(ncol = 2))+
    ggtitle(gsub("_", " ", names(filtered_dataset[,2:(length(names(filtered_dataset))-3)])[data]))+
    theme(plot.subtitle=element_text(size=10, hjust=0.5),
          strip.text.x = element_text(hjust = 0.5, size = 10), legend.position = "right",
          title = element_text(size=10, hjust=0.5),
          axis.title.x = element_text(size=12), 
          axis.title.y = element_text(size=12))
    #labs(tag = "B")
})
  
  rad_plots
  
}


plot_shape_differences(rad_info, geno_shape_diffs_v1$cols)

plot_volumes_only(rad_info)

```

```{r, fig.height=3.5, fig.width=5}
plot_shape_differences(rad_info_v2, geno_shape_diffs_v2$cols)
plot_volumes_only(rad_info_v2)

```


```{r, fig.height=4, fig.width=5.5}
plot_shape_differences(rad_info, back_shape_diffs_v1$cols)

```


```{r, fig.height=4, fig.width=5.5}
plot_shape_differences(rad_info_v2, back_shape_diffs_v2$cols)
```


```{r}

cluster_df <- data.frame(matrix(unlist(split_names), nrow=length(split_names), byrow=TRUE))
  colnames(cluster_df) <- c("Filter", "Type", "Stat", "Org")
  complete_df <- rbind(complete_df, cluster_df)
  
  org_counts <- table(complete_df$Org)
  org_proportions <- prop.table(org_counts)
  
  # Count and proportion of interactions
  interaction_counts <- table(cluster_df$Filter, cluster_df$Type, cluster_df$Org)
  interaction_proportions <- prop.table(interaction_counts)
  
  # Convert interaction_proportions to a data frame
  interaction_df <- as.data.frame.table(interaction_proportions)
  colnames(interaction_df) <- c("Filter", "Type", "Org", "Proportion")



significant_feats_means <- significant_feats %>% filter(vol %in% sev_HPE_bros) %>% select_if(is.numeric) %>% colMeans()
  
cluster_df <- create_cluster_df(significant_feats_means)

cluster_df$VolMean <- significant_feats_means

pos_or_neg <- ifelse(significant_feats_means < 1, "Negative", "Positive")


cluster_df$Correlation <- pos_or_neg
  
# Create the plot for this iteration and store it in the list

org_type_levels <- c("glrlm.brain lateral ventricle","firstorder.forebrain anteroventral region", "glcm.forebrain anteroventral region","gldm.forebrain anteroventral region","glrlm.forebrain anteroventral region","glszm.forebrain anteroventral region", "ngtdm.forebrain anteroventral region",    "shape.forebrain anteroventral region","gldm.midbrain","glrlm.midbrain", "ngtdm.midbrain", "firstorder.vomeronasal cavity")

cluster_df$Org_Type <- factor(interaction(cluster_df$Type, cluster_df$Org), levels=org_type_levels)

split_by_corr <- split(cluster_df, cluster_df$Correlation)

my_palette <- hcl.colors(7, palette = "Dark3")

type_colors <- setNames(my_palette, c("firstorder","glcm","gldm","glrlm","glszm","ngtdm", "shape"))




ggplot(mapping=aes(x = Type, y = log2(VolMean), col=Correlation)) +
  #geom_point(data=all_df, width = 0.5, position = position_dodge(width = 0.75), alpha=0.5)+
  geom_boxplot(data = split_by_corr$Negative, width = 0.5, position = position_dodge(width = 0.75)) +
  #geom_point(data = split_by_corr$Negative, width = 0.5, position = position_dodge(width = 0.75))+
  geom_boxplot(data = split_by_corr$Positive, width = 0.5, position = position_dodge(width = 0.75)) +
  #geom_point(data = split_by_corr$Positive, width = 0.5, position = position_dodge(width = 0.75)) +
  labs(title = "Statistically Significant Features in Mild and Severe HPE embryos", x = "Feature Type", 
       y = expression("Log"[2] * "(Mean Measurement Ratio Between HPE and Non-HPE embryos)"), color = "Association of Feature") +
  theme_minimal()+
  facet_wrap(~Org, scales = "fixed", nrow = 1)+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1), legend.position = "bottom") +
  #scale_y_continuous(breaks = c(0, 1, 2, 3, 4, 5, 6, 7, 8)) +
  #facet_zoom(ylim = c(0, 2), zoom.data = ifelse((VolMean <= 2), NA, FALSE)) +
  #cale_color_manual(values = c("blue", "red"))+
  scale_y_continuous(limits=c(-2,2))+
  scale_color_manual(values = c("blue", "red"))+
  #geom_segment(aes(x = "Org1_TypeB", xend = "Org2_TypeA", y = -Inf, yend = Inf), linetype = "dashed") 
  #scale_color_manual(values = type_colors)
  #facet_zoom(ylim = c(0, 2), zoom.data = ifelse((VolMean <= 2)&(Org == 'forebrain anteroventral region'), NA, FALSE))+
  stat_summary(data = split_by_corr$Negative, fun.data = n_fun_neg, geom = "text", col="blue", vjust = 2)+
  stat_summary(data = split_by_corr$Positive, fun.data = n_fun_pos, geom = "text", col="red", vjust = -1)









plot_list <- list()
complete_df <- data.frame(matrix(ncol=4, nrow=0))
colnames(complete_df) <- c("Filter", "Type", "Stat", "Org")
# Iterate over filtered_classes from 1 to 7
for (i in 1:7) {
  # Filter the classes
  filtered_classes <- sort(classes[classes == i])
  
  # Print the information about the filtered classes
  message(paste(length(filtered_classes), " of ", length(classes), " features (", round((length(filtered_classes) / length(classes)) * 100, 2), "%)", sep = ""))
  
  # Split the names
  split_names <- strsplit(names(filtered_classes), "_")
  split_names <- lapply(split_names, function(x) {
    if ("wavelet" %in% x) {x <- x[c(-1)]}
    return(x)})
  
  
  split_names <- lapply(split_names, merge_after_third)
  
  # Create the cluster_df
  cluster_df <- data.frame(matrix(unlist(split_names), nrow=length(split_names), byrow=TRUE))
  colnames(cluster_df) <- c("Filter", "Type", "Stat", "Org")
  complete_df <- rbind(complete_df, cluster_df)
  
  # Count and proportion of occurrences for the "Org" column
  org_counts <- table(complete_df$Org)
  org_proportions <- prop.table(org_counts)
  
  # Count and proportion of interactions
  interaction_counts <- table(cluster_df$Filter, cluster_df$Type, cluster_df$Org)
  interaction_proportions <- prop.table(interaction_counts)
  
  # Convert interaction_proportions to a data frame
  interaction_df <- as.data.frame.table(interaction_proportions)
  colnames(interaction_df) <- c("Filter", "Type", "Org", "Proportion")
  
  # Create the plot for this iteration and store it in the list
  plot_list[[i]] <- ggplot(interaction_df, aes(x = Filter, y = Proportion, fill = Type)) +
    geom_bar(stat = "identity", position = "stack") +
    labs(title = paste("Proportions by Filter and Type (Cluster =", i, ")", sep = " "), x = "Filter", y = "Proportion", fill = "Type") +
    facet_wrap(~Org, scales = "fixed", nrow = 2) +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
}

```
Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
```{r}
all_info <- rad_info

rad_info <- rad_info %>% filter(Genotype=="WT", Background == "C3H")

numbers <- unique(sub(".*__", "", names(rad_info)[-1]))

# Create a list to store the split datasets
split_datasets <- list()

# Loop through each number and subset the columns based on the number
for (num in numbers) {
  cols <- grep(paste0("__", num, "$"), names(rad_info))
  split_datasets[[num]] <- rad_info[, c(1, cols)]
}

rad_info_matrix <- data.frame(cbind(split_datasets$`1`, split_datasets$`3`)) %>% select_if(is.numeric) %>% na.omit() %>% as.matrix()

# , split_datasets$`17`, split_datasets$`18`

# Calculate the correlation matrix using Pearson coefficient
cor_matrix <- cor(rad_info_matrix, method = "pearson")

# Convert correlation to distance
dist_matrix <- as.dist(1 - cor_matrix)


consensus_obj <- ConsensusClusterPlus(
  dist_matrix,
  distance = "pearson",
  maxK = 10,  # Maximum number of clusters to consider
  reps = 50,  # Number of resampling iterations - turn up if needed
  pItem = 0.8,  # Proportion of items to sample on each iteration
  pFeature = 1,  # Proportion of features to sample on each iteration
  clusterAlg = "hc",
  finalLinkage = "ward.D",# Use Ward's algorithm
  innerLinkage = "ward.D",# Use Ward's algorithm
  verbose= T,
  plot = TRUE  # Plot the consensus clustering results
)

```


```{r}
classes <- consensus_obj[[7]]$consensusClass
# Use filter on the extracted data frame or tibble
filtered_classes <- sort(classes[classes==1])


paste(length(filtered_classes), " of ", length(classes), " features (", round((length(filtered_classes)/length(classes))*100,2), "%)", sep="")

```

```{r }
plot_list <- list()


complete_df <- data.frame(matrix(ncol=4, nrow=0))
colnames(complete_df) <- c("Filter", "Type", "Stat", "Org")
# Iterate over filtered_classes from 1 to 7
for (i in 1:7) {
  # Filter the classes
  filtered_classes <- sort(classes[classes == i])
  
  # Print the information about the filtered classes
  message(paste(length(filtered_classes), " of ", length(classes), " features (", round((length(filtered_classes) / length(classes)) * 100, 2), "%)", sep = ""))
  
  # Split the names
  split_names <- strsplit(names(filtered_classes), "_")
  split_names <- sapply(split_names, function(x) if (length(x) == 6) x[c(-1, -5)] else x[-4])
  
  # Create the cluster_df
  cluster_df <- data.frame(t(split_names))
  
  colnames(cluster_df) <- c("Filter", "Type", "Stat", "Org")
  complete_df <- rbind(complete_df, cluster_df)
  
  # Count and proportion of occurrences for the "Org" column
  org_counts <- table(cluster_df$Org)
  org_proportions <- prop.table(org_counts)
  
  # Count and proportion of interactions
  interaction_counts <- table(cluster_df$Filter, cluster_df$Type, cluster_df$Org)
  interaction_proportions <- prop.table(interaction_counts)
  
  # Convert interaction_proportions to a data frame
  interaction_df <- as.data.frame.table(interaction_proportions)
  colnames(interaction_df) <- c("Filter", "Type", "Org", "Proportion")
  
  # Create the plot for this iteration and store it in the list
  plot_list[[i]] <- ggplot(interaction_df, aes(x = Filter, y = Proportion, fill = Type)) +
    geom_bar(stat = "identity", position = "stack") +
    labs(title = paste("Proportions by Filter and Type (Cluster =", i, ")", sep = " "), x = "Filter", y = "Proportion", fill = "Type") +
    facet_wrap(~Org, scales = "fixed", nrow = 1) +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
}

# Print the plots
for (i in 1:7) {
  print(plot_list[[i]])
}

```
# all feats - non clustered
```{r, fig.width=10}
  
# Count and proportion of interactions
interaction_counts <- table(complete_df$Filter, complete_df$Type, complete_df$Org)
interaction_proportions <- prop.table(interaction_counts)
  
# Convert interaction_proportions to a data frame
interaction_df <- as.data.frame.table(interaction_proportions)
colnames(interaction_df) <- c("Filter", "Type", "Org", "Proportion")
  
# Create the plot for this iteration and store it in the list
ggplot(interaction_df, aes(x = Filter, y = Proportion, fill = Type)) +
  geom_bar(stat = "identity", position = "stack") +
  labs(title = paste("Proportions by Filter and Type (all_clusters)", sep = " "), x = "Filter", y = "Proportion", fill = "Type") +
  facet_wrap(~Org, scales = "fixed", nrow = 1) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))

```

##Significant feats only

```{r }
#setting up dataset





```

```{r}




filtered_dataset <- rad_info[, colnames(rad_info) %in% colnames(significant_feats)]


weird_dataset <- significant_feats[, !(colnames(significant_feats) %in% colnames(rad_info))]

filtered_dataset$vol <- rad_info$vol


filtered_dataset <- merge(filtered_dataset, staging_info)

filtered_dataset

```


```{r}
filtered_matrix_s <- filtered_dataset %>% select_if(is.numeric) %>% dplyr::select(-WEV) %>% remove_constant() %>% as.matrix()

cor_matrix_sf_s <- cor(filtered_matrix_s, method = "pearson")

# Convert correlation to distance
dist_matrix_sf_s <- as.dist(1 - cor_matrix_sf_s)

consensus_obj_v3 <- ConsensusClusterPlus(
  dist_matrix_sf_s,
  distance = "pearson",
  maxK = 10,  # Maximum number of clusters to consider
  reps = 50,  # Number of resampling iterations
  pItem = 0.8,  # Proportion of items to sample on each iteration
  pFeature = 1,  # Proportion of features to sample on each iteration
  clusterAlg = "hc",
  finalLinkage = "ward.D",# Use Ward's algorithm
  innerLinkage = "ward.D",# Use Ward's algorithm
  verbose= F,
  plot = TRUE  # Plot the consensus clustering results
)
```

```{r}
classes <- consensus_obj_v3[[7]]$consensusClass
# Use filter on the extracted data frame or tibble
filtered_classes <- sort(classes[classes==1])


paste(length(filtered_classes), " of ", length(classes), " features (", round((length(filtered_classes)/length(classes))*100,2), "%)", sep="")

```

```{r fig.width=10, fig.height=6}
# Define a function to merge elements after the third element
merge_after_third <- function(vec) {
  vec[4] <- paste(vec[4:length(vec)], collapse = " ")
  vec <- vec[1:4]
  return(vec)
}

plot_list <- list()
complete_df <- data.frame(matrix(ncol=4, nrow=0))
colnames(complete_df) <- c("Filter", "Type", "Stat", "Org")
# Iterate over filtered_classes from 1 to 7
for (i in 1:7) {
  # Filter the classes
  filtered_classes <- sort(classes[classes == i])
  
  # Print the information about the filtered classes
  message(paste(length(filtered_classes), " of ", length(classes), " features (", round((length(filtered_classes) / length(classes)) * 100, 2), "%)", sep = ""))
  
  # Split the names
  split_names <- strsplit(names(filtered_classes), "_")
  split_names <- lapply(split_names, function(x) {
    if ("wavelet" %in% x) {x <- x[c(-1)]}
    return(x)})
  
  
  split_names <- lapply(split_names, merge_after_third)
  
  # Create the cluster_df
  cluster_df <- data.frame(matrix(unlist(split_names), nrow=length(split_names), byrow=TRUE))
  colnames(cluster_df) <- c("Filter", "Type", "Stat", "Org")
  complete_df <- rbind(complete_df, cluster_df)
  
  # Count and proportion of occurrences for the "Org" column
  org_counts <- table(complete_df$Org)
  org_proportions <- prop.table(org_counts)
  
  # Count and proportion of interactions
  interaction_counts <- table(cluster_df$Filter, cluster_df$Type, cluster_df$Org)
  interaction_proportions <- prop.table(interaction_counts)
  
  # Convert interaction_proportions to a data frame
  interaction_df <- as.data.frame.table(interaction_proportions)
  colnames(interaction_df) <- c("Filter", "Type", "Org", "Proportion")
  
  # Create the plot for this iteration and store it in the list
  plot_list[[i]] <- ggplot(interaction_df, aes(x = Filter, y = Proportion, fill = Type)) +
    geom_bar(stat = "identity", position = "stack") +
    labs(title = paste("Proportions by Filter and Type (Cluster =", i, ")", sep = " "), x = "Filter", y = "Proportion", fill = "Type") +
    facet_wrap(~Org, scales = "fixed", nrow = 2) +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
}

# Print the plots
for (i in 1:7) {
  print(plot_list[[i]])
}

```


```{r, fig.width=12, fig.height=8}
  
# Count and proportion of interactions
interaction_counts <- table(complete_df$Filter, complete_df$Type, complete_df$Stat, complete_df$Org)
interaction_proportions <- prop.table(interaction_counts)
  
# Convert interaction_proportions to a data frame
interaction_df <- as.data.frame.table(interaction_counts)
colnames(interaction_df) <- c("Filter", "Type", "Stat", "Org", "Proportion")

  
# Create the plot for this iteration and store it in the list
ggplot(interaction_df, aes(x = Type, y = Proportion, fill = Filter)) +
  geom_bar(stat = "identity", position = "stack") +
  labs(title = paste("Features Significant in both mild and severe HPE embryos", sep = " "), x = "Statistic", y = "Frequency", fill = "Type") +
  facet_wrap(~Org, scales = "fixed", nrow = 2) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))

```


```{r}

all_feats_use <- all_feats %>% filter(vol %in% sev_HPE_bros)%>% select_if(is.numeric)

all_feats_use <- all_feats_use[,!(colnames(all_feats_use) %in% c(cols_outside_range, cols_outside_range2))]

all_means_vol <-all_feats_use %>% colMeans()


split_names <- strsplit(names(all_feats_use), "_")

split_names <- lapply(split_names, function(x) {
    if ("wavelet" %in% x) {x <- x[c(-1)]}
    return(x)})

split_names <- lapply(split_names, merge_after_third)
  
  # Create the cluster_df
all_df <- data.frame(matrix(unlist(split_names), nrow=length(split_names), byrow=TRUE))

colnames(all_df) <- c("Filter", "Type", "Stat", "Org")

all_df$VolMean <- all_means_vol


pos_or_neg <- "Not Significant"

all_df$Correlation <- pos_or_neg

all_df

#all_df <- all_df %>% filter(Org=="forebrain anteroventral region")

```


```{r, fig.width=8, fig.height=6}
# get mean_vol_ratio across HPE bryos

significant_feats_means <- significant_feats %>% filter(vol %in% sev_HPE_bros) %>% select_if(is.numeric) %>% colMeans()
  

split_names <- strsplit(names(significant_feats_means), "_")

split_names <- lapply(split_names, function(x) {
    if ("wavelet" %in% x) {x <- x[c(-1)]}
    return(x)})

split_names <- lapply(split_names, merge_after_third)
  
  # Create the cluster_df
cluster_df <- data.frame(matrix(unlist(split_names), nrow=length(split_names), byrow=TRUE))
colnames(cluster_df) <- c("Filter", "Type", "Stat", "Org")
  

cluster_df$VolMean <- significant_feats_means
pos_or_neg <- ifelse(significant_feats_means < 1, "Negative", "Positive")




cluster_df$Correlation <- pos_or_neg
  
# Create the plot for this iteration and store it in the list

org_type_levels <- c("glrlm.brain lateral ventricle","firstorder.forebrain anteroventral region", "glcm.forebrain anteroventral region","gldm.forebrain anteroventral region","glrlm.forebrain anteroventral region","glszm.forebrain anteroventral region", "ngtdm.forebrain anteroventral region",    "shape.forebrain anteroventral region","gldm.midbrain","glrlm.midbrain", "ngtdm.midbrain", "firstorder.vomeronasal cavity")

cluster_df$Org_Type <- factor(interaction(cluster_df$Type, cluster_df$Org), levels=org_type_levels)

split_by_corr <- split(cluster_df, cluster_df$Correlation)

my_palette <- hcl.colors(7, palette = "Dark3")

type_colors <- setNames(my_palette, c("firstorder","glcm","gldm","glrlm","glszm","ngtdm", "shape"))




ggplot(mapping=aes(x = Type, y = log2(VolMean), col=Correlation)) +
  #geom_point(data=all_df, width = 0.5, position = position_dodge(width = 0.75), alpha=0.5)+
  geom_boxplot(data = split_by_corr$Negative, width = 0.5, position = position_dodge(width = 0.75)) +
  #geom_point(data = split_by_corr$Negative, width = 0.5, position = position_dodge(width = 0.75))+
  geom_boxplot(data = split_by_corr$Positive, width = 0.5, position = position_dodge(width = 0.75)) +
  #geom_point(data = split_by_corr$Positive, width = 0.5, position = position_dodge(width = 0.75)) +
  labs(title = "Statistically Significant Features in Mild and Severe HPE embryos", x = "Feature Type", 
       y = expression("Log"[2] * "(Mean Measurement Ratio Between HPE and Non-HPE embryos)"), color = "Association of Feature") +
  theme_minimal()+
  facet_wrap(~Org, scales = "fixed", nrow = 1)+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1), legend.position = "bottom") +
  #scale_y_continuous(breaks = c(0, 1, 2, 3, 4, 5, 6, 7, 8)) +
  #facet_zoom(ylim = c(0, 2), zoom.data = ifelse((VolMean <= 2), NA, FALSE)) +
  #cale_color_manual(values = c("blue", "red"))+
  scale_y_continuous(limits=c(-2,2))+
  scale_color_manual(values = c("blue", "red"))+
  #geom_segment(aes(x = "Org1_TypeB", xend = "Org2_TypeA", y = -Inf, yend = Inf), linetype = "dashed") 
  #scale_color_manual(values = type_colors)
  #facet_zoom(ylim = c(0, 2), zoom.data = ifelse((VolMean <= 2)&(Org == 'forebrain anteroventral region'), NA, FALSE))+
  stat_summary(data = split_by_corr$Negative, fun.data = n_fun_neg, geom = "text", col="blue", vjust = 2)+
  stat_summary(data = split_by_corr$Positive, fun.data = n_fun_pos, geom = "text", col="red", vjust = -1)
  
  
  #expand_limits(y = c(0, 8.5)) 



```



```{r}

test_all_info <- all_info %>% dplyr::select(where(is.numeric))

all_info_df <- create_cluster_df(test_all_info)

all_info_df$Org <- mapping$label_name[match(as.numeric(all_info_df$Org), mapping$label)]


all_info_df <- na.omit(all_info_df)


all_info_df$Org <- gsub("_", " ", all_info_df$Org)


complete_df_counts <- table(complete_df$Filter, complete_df$Type, complete_df$Org, useNA = "ifany") %>% as.data.frame()



interaction_counts_all <- table(all_info_df$Filter, all_info_df$Type, all_info_df$Org)

interaction_counts_test <- table(all_info_df$Filter, all_info_df$Org)

interaction_counts_all <- data.frame(interaction_counts_all)

colnames(interaction_counts_all) <- c("Filter", "Type", "Org", "Total")

colnames(complete_df_counts) <- c("Filter", "Type", "Org", "Freq")


counts_table <- merge(interaction_counts_all, complete_df_counts, all.x=T, all.y=T, by=c("Filter", "Type","Org"))

counts_table[is.na(counts_table)] <- 0


# correct for size factors:

# get total cell counts and divide by global mean
#totals <- colSums(select_if(interaction_counts, is.numeric)) 

#size_factors <- interaction_counts_all$Freq / mean(interaction_counts_all$Freq)

#cont_table_xtabs <- xtabs(Frequency ~ Cell_Type + Genotype, data = cell_counts_long_v2)

# just replaces the data with the normalised data
#dataset[2:9] <- dataset[2:9]/size_factors[col(dataset[2:9])]
counts_table
all_info_df

```


```{r}

counts_table <- counts_table %>% mutate(Prop=Freq/Total)

counts_table <- counts_table[complete.cases(counts_table), ]

#kruskal.test(Prop ~ Org, data = counts_table)

test <- counts_table %>% filter(Org=='forebrain anteroventral region')

model <-aov(Prop ~ Filter*Type, data = test)

anova(model)

# Perform the post-hoc test
#posthoc <- glht(model, linfct = mcp(`Type:Filter` = "Tukey"))

# Get compact letter display
#cld(posthoc)
test <- test %>% mutate(Non_Sign_Freq = Total-Freq)


# Loop over each type and perform Fisher's exact test
sign_table <- xtabs(Freq ~ Type, data = test)

non_sign_table <- xtabs(Non_Sign_Freq ~ Type, data = test)

contingency_table <- rbind(sign_table, non_sign_table)

contingency_table


proportions <- xtabs(Prop ~ Filter + Type, data = test)



results <- apply(proportions, 2, function(col) {
  binom.test(sum(col > 0), length(col), p=0.05, alternative="greater")
})

results

p_values <- sapply(results, function(x) x$p.value)
p_values

fisher_result <- fisher.test(contingency_table)


fisher_result

p_values <- sapply(fisher_results, function(x) x$p.value)
p_values
```



```{r, fig.height=10, fig.width=14}


# compute mean and standard error of the mean by subgroup
summary_stat <- summarySE(counts_table,
  measurevar = "Prop",
  groupvars = c("Type", "Org")
)

# plot mean and standard error of the mean
ggplot(
  subset(summary_stat, !is.na(Type)), # remove NA level for Type
  aes(x = Org, y = Prop, colour = Type, fill=Type)
) +
  geom_errorbar(aes(ymin = Prop - se, ymax = Prop + se), # add error bars
    width = 0.1 # width of error bars
  ) +
  geom_col() +
  labs(y = "Proportion of Features")+
  facet_wrap(~Type, ncol = 2)+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))



```


```{r}

model2 <-aov(Prop ~ Filter*Type, data = counts_table)

summary(model2)

#test <- TukeyHSD(model2, which = "Filter:Type")

# only type is significant
# Perform the post-hoc test

model3 <- aov(Prop ~ Type, data = counts_table)
posthoc
posthoc <- glht(model3, linfct = mcp(Type="Tukey"))

# Get compact letter display
cld(posthoc)


```



```{r fig.width=30}

model4 <- aov(Prop ~ Org*Type, data = counts_table)

summary(model4)

test <- TukeyHSD(model4, which = "Org:Type")

#library(effects)

#plot(allEffects(test))


library(Rmisc)

# compute mean and standard error of the mean by subgroup
summary_stat <- summarySE(counts_table,
  measurevar = "Prop",
  groupvars = c("Org", "Type")
)

# plot mean and standard error of the mean
ggplot(
  subset(summary_stat, !is.na(Type)), # remove NA level for Type
  aes(x = Org, y = Prop, colour = Type)
) +
  geom_errorbar(aes(ymin = Prop - se, ymax = Prop + se), # add error bars
    width = 0.1 # width of error bars
  ) +
  geom_point() +
  labs(y = "Mean of body mass (g)")



with(
  counts_table,
  interaction.plot(Org, Type, Prop)
)

library(multcompView)


# Assuming test is your Tukey's HSD test object
cld_results <- multcompLetters(test)

# Print the compact letter display
print(cld_results)
```